---
title: "Coste-eficacia de PrEP en España"
author: "Philip Wikman"
date: "15 de mayo de 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(dplyr)
library(forcats)
source("QALYCostP.R")
source("HIVSIM04.R")
source("QalyCalc.R")
source("CostCalc.R")
set.seed(123)

```

# Load best fit parameters
```{r}
load("BestParam_LCA")
```

# OWA sensitivity analysis
```{r}

DistEdad<-vector(length=85)
DistEdad[1:10]<-0.114106384/10
DistEdad[11:20]<-0.116645332/10
DistEdad[21:30]<-0.281029342/10
DistEdad[31:40]<-0.30552628/10
DistEdad[41:50]<-0.112127906/10
DistEdad[51:85]<-0.070564755/35

Age<-85
years<-20

NoSem<-52
NumHSH<-892955-Bestparam[1] #(INE)
NumHSHVIH<-Bestparam[1]  #Encuesta hospitalaria

ACD4<-Bestparam[2] #Distribucion de los pacientes por rango de CD4 <200
I8CD4<-Bestparam[3] #200-350
I7CD4<-Bestparam[4] #350-500
Rest<-Bestparam[5]   #>500
PropTR<-Bestparam[6]

#Values 
G<-Bestparam[7]  #Population growth rate 1/1000 anually
#L<-0.05/52   #Force of infection
m<-read.csv("MortPobGen.csv", header=TRUE, sep=";")  #Mortality general population
mVIH235<-Bestparam[8] #Alejos et al Medicine 2016
mVIH35<-Bestparam[9]   #Alejos et al Medicine 2016
mAIDS<-Bestparam[10]  #Parastu et al PLOSone 2018
Cvh<-Bestparam[11] #Partner change rate in the very high group 18-123/year Nichols et al. 2016
Ch<-Bestparam[12]     #Partner change rate in the high group 5-18/year Nichols et al. 2016
Cl<-Bestparam[13]   #Partner change rate in the low group 0.5-5/year Nichols et al. 2016
Cvl<-Bestparam[14]  #Partner change rate in the very low group 0.04-0.5/year Nichols et al. 2016
nvh<-Bestparam[15]     #Proportion of the total population in each group 5-15% Nichols et al. 2016
nh<-Bestparam[16]     #30-50% Nichols et al. 2016
nl<-Bestparam[17]     #10-35% Nichols et al. 2016
nvl<-Bestparam[18]    #4-46%

B<-Bestparam[19]  #per partnership transmissibility Nichols et al 2016.
I12<-Bestparam[20] #1 month duration in stage 1 of HIV infection
I23<-Bestparam[21] #1 month duration in stage 2 of HIV infection
I34<-Bestparam[22] #1 month duration in stage 3 of HIV infection
I45<-Bestparam[23] #3 month duration in stage 4 of HIV infection
I55<-Bestparam[25] #3 month duration in stage 5 of HIV infection
I56<-Bestparam[26] #3 month duration in stage 6 of HIV infection
I67<-Bestparam[27] #Chronic duration in stage 7 of HIV infection
I78<-Bestparam[28] #Chronic duration in stage 9 of HIV infection
I89<-Bestparam[29] #Chronic duration in stage 10 of HIV infection

PTr<-c(Bestparam[30],Bestparam[31],Bestparam[32]) #Nuñez et al AIDS 2018     
                                            #200-500->500

Woff<-1-exp(-0.12/52) #Proportion of people who go off PrEP 30% anually
W<-1-exp(-0.3/52)    #Proportion of people who go on PrEP 30% anually
RiskRed<-1-0.86 # 0.86 for TDF, 0.934 for TAF and 0.952 for CBV 0.96 for LCA
WAIDS<-0.7/52  
WHIV<-0.84/52
WM350<-0.94/52
WTREAT<-0.96/52    
WSusceptible<-1/52
Treatcost<-188.54
AIDScost<-19000/52
PrEPcost<-26.94 # TDF/FTC 26.94, TAF/FTC 137.5, CAB 178.95

OWSAmat<-matrix(ncol=4, nrow=31, dimnames=list(NULL, c("QALYsl", "Costsl", "QALYsh", "Costsh")))
```

## 1. NumHSHVIH
### Low estimate
```{r}
NumHSHVIH<-Bestparam[1]-Bestparam[1]*0.2
NumHSH<-892955-NumHSHVIH

Q<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH,
                 ACD4, I8CD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mAIDS, mVIH235, mVIH35, mTr, 
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I55, 
                 I56, I67, 
                 I78, I89, PTr, years)

l1<-QALYCostP(Q)
l1
OWSAmat[1,1:2]<-l1
OWSAmat
```

### High estimate
```{r}

NumHSHVIH<-Bestparam[1]+Bestparam[1]*0.2
NumHSH<-892955-NumHSHVIH

Q<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I8CD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mAIDS, mVIH235, mVIH35, mTr, 
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I55, 
                 I56, I67, 
                 I78, I89, PTr, years)

h1<-QALYCostP(Q)
OWSAmat[1,3:4]<-h1
OWSAmat

NumHSHVIH<-Bestparam[1]
NumHSH<-892955-NumHSHVIH
```

## 2. % pacientes con CD4 menor de 200
### Low estimate
```{r}
ACD4<-Bestparam[2]-Bestparam[2]*0.2
Q<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, 
                 I8CD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mAIDS, mVIH235, mVIH35, mTr, 
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I55, 
                 I56, I67, 
                 I78, I89, PTr, years)
l2<-QALYCostP(Q)
OWSAmat[2,1:2]<-l2
```

### High estimate
```{r}
ACD4<-Bestparam[2]+Bestparam[2]*0.2

Q<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4<-Bestparam[2]+Bestparam[2]*0.2, I8CD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mAIDS, mVIH235, mVIH35, mTr, 
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I55, 
                 I56, I67, 
                 I78, I89, PTr, years)

h2<-QALYCostP(Q)
OWSAmat[2,3:4]<-h2
OWSAmat
ACD4<-Bestparam[2]
```

## 3. % pacientes con CD4 entre 200-350
### Low estimate
```{r}
I8CD4<-Bestparam[3]-Bestparam[3]*0.2
Q<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I8CD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mAIDS, mVIH235, mVIH35, mTr, 
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I55, 
                 I56, I67, 
                 I78, I89, PTr, years)
l3<-QALYCostP(Q)
OWSAmat[3,1:2]<-l3
```

### High estimate
```{r}
I8CD4<-Bestparam[3]+Bestparam[3]*0.2
Q<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I8CD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mAIDS, mVIH235, mVIH35, mTr, 
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I55, 
                 I56, I67, 
                 I78, I89, PTr, years)


h3<-QALYCostP(Q)
OWSAmat[3,3:4]<-h3
OWSAmat
I8CD4<-Bestparam[3]
```

## 4. % pacientes con CD4 entre 350-500
### Low estimate
```{r}
I7CD4<-Bestparam[4]-Bestparam[4]*0.2
Q<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I8CD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mAIDS, mVIH235, mVIH35, mTr, 
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I55, 
                 I56, I67, 
                 I78, I89, PTr, years)
l4<-QALYCostP(Q)
OWSAmat[4,1:2]<-l4
```

### High estimate
```{r}
I7CD4<-Bestparam[4]+Bestparam[4]*0.2
Q<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I8CD4, I7CD4=Bestparam[4]+Bestparam[4]*0.2, Rest, 
                 G, Woff, W, 
                 m, mAIDS, mVIH235, mVIH35, mTr, 
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I55, 
                 I56, I67, 
                 I78, I89, PTr, years)

h4<-QALYCostP(Q)
OWSAmat[4,3:4]<-h4
OWSAmat
I7CD4=Bestparam[4]
```

## 5. % pacientes con CD4 mayor de 500
### Low estimate
```{r}
Rest<-Bestparam[5]-Bestparam[5]*0.2
Q<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I8CD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mAIDS, mVIH235, mVIH35, mTr, 
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I55, 
                 I56, I67, 
                 I78, I89, PTr, years)
l5<-QALYCostP(Q)
OWSAmat[5,1:2]<-l5
```

### High estimate
```{r}
Rest<-Bestparam[5]+Bestparam[5]*0.2
Q<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I8CD4, I7CD4, Rest=Bestparam[5]+Bestparam[5]*0.2, 
                 G, Woff, W, 
                 m, mAIDS, mVIH235, mVIH35, mTr, 
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I55, 
                 I56, I67, 
                 I78, I89, PTr, years)

h5<-QALYCostP(Q)
OWSAmat[5,3:4]<-h5
OWSAmat
Rest<-Bestparam[5]
```
## 6. Proportion on treatment
### Low estimate
```{r}
PropTR<-Bestparam[6]-Bestparam[6]*0.2
Q<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I8CD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mAIDS, mVIH235, mVIH35, mTr, 
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I55, 
                 I56, I67, 
                 I78, I89, PTr, years, PropTR)
l6<-QALYCostP(Q)
OWSAmat[6,1:2]<-l6
```

### High estimate
```{r}
PropTR<-Bestparam[6]+Bestparam[6]*0.2
Q<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I8CD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mAIDS, mVIH235, mVIH35, mTr, 
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I55, 
                 I56, I67, 
                 I78, I89, PTr, years, PropTR)

h6<-QALYCostP(Q)
OWSAmat[6,3:4]<-h6
OWSAmat
PropTR<-Bestparam[6]
```

## 7. Proportion on treatment at start
### Low estimate
```{r}
G<-Bestparam[7]-Bestparam[7]*0.2
Q<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I8CD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mAIDS, mVIH235, mVIH35, mTr, 
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I55, 
                 I56, I67, 
                 I78, I89, PTr, years,PropTR)
l7<-QALYCostP(Q)
OWSAmat[7,1:2]<-l7
```

### High estimate
```{r}
G<-Bestparam[7]+Bestparam[7]*0.2
Q<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I8CD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mAIDS, mVIH235, mVIH35, mTr, 
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I55, 
                 I56, I67, 
                 I78, I89, PTr, years,PropTR)
h7<-QALYCostP(Q)
OWSAmat[7,3:4]<-h7
G<-Bestparam[7]
```

## 8. Mortality HIV 200-350 CD4
### Low estimate
```{r}
mVIH235=Bestparam[8]-Bestparam[8]*0.2
Q<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I8CD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mAIDS, mVIH235, mVIH35, 
                 mTr, 
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I55, 
                 I56, I67, 
                 I78, I89, PTr, years,PropTR)
l8<-QALYCostP(Q)
OWSAmat[8,1:2]<-l8
```

### High estimate
```{r}
mVIH235=Bestparam[8]+Bestparam[8]*0.2
Q<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I8CD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mAIDS, mVIH235, mVIH35, 
                 mTr, 
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I55, 
                 I56, I67, 
                 I78, I89, PTr, years,PropTR)
h8<-QALYCostP(Q)
OWSAmat[8,3:4]<-h8
OWSAmat
mVIH235<-Bestparam[8]
```

## 9. Mortality HIV >350 CD4
### Low estimate
```{r}
mVIH35=Bestparam[9]-Bestparam[9]*0.2
Q<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I8CD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mAIDS, mVIH235, mVIH35, 
                 mTr, 
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I55, 
                 I56, I67, 
                 I78, I89, PTr, years,PropTR)
l9<-QALYCostP(Q)
OWSAmat[9,1:2]<-l9
```

### High estimate
```{r}
mVIH35=Bestparam[9]+Bestparam[9]*0.2
Q<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I8CD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mAIDS, mVIH235, mVIH35,
                 mTr, 
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I55, 
                 I56, I67, 
                 I78, I89, PTr, years,PropTR)
h9<-QALYCostP(Q)
OWSAmat[9,3:4]<-h9
OWSAmat
mVIH35<-Bestparam[9]
```

## 10. Mortality AIDS
### Low estimate
```{r}
mAIDS=(Bestparam[10]-Bestparam[10]*0.2)
Q<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I8CD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mAIDS, mVIH235,
                 mVIH35, mTr, 
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I55, 
                 I56, I67, 
                 I78, I89, PTr, years,PropTR)

l10<-QALYCostP(Q)
OWSAmat[10,1:2]<-l10
```

### High estimate
```{r}
mAIDS=Bestparam[10]+Bestparam[10]*0.2
Q<-HIVSIMPREP(Age=85, NoSem=52, NumHSH, NumHSHVIH, 
                 ACD4, I8CD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mAIDS, mVIH235, mVIH35,
                 mTr, 
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I55, 
                 I56, I67, 
                 I78, I89, PTr, years=40,PropTR)
h10<-QALYCostP(Q)
OWSAmat[10,3:4]<-h10
mAIDS<-Bestparam[10]
```

## 11. Cvh Partner change rate in very hig risk group
### Low estimate
```{r}
Cvh<-Bestparam[11]-Bestparam[11]*0.2
Q<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I8CD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mAIDS, mVIH235, mVIH35, mTr, 
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, I45, I55, I56, I67, 
                 I78, I89, PTr, years,PropTR)
l11<-QALYCostP(Q)
OWSAmat[11,1:2]<-l11
```

### High estimate
```{r}
Cvh<-Bestparam[11]+Bestparam[11]*0.2
Q<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I8CD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mAIDS, mVIH235, mVIH35, mTr, 
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I55, 
                 I56, I67, 
                 I78, I89, PTr, years,PropTR)
h11<-QALYCostP(Q)
OWSAmat[11,3:4]<-h11
OWSAmat
Cvh<-Bestparam[11]
```

## 12. Ch Partner change rate in high risk group
### Low estimate
```{r}
Ch<-Bestparam[12]-Bestparam[12]*0.2
Q<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I8CD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mAIDS, mVIH235, mVIH35, mTr, 
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I55, 
                 I56, I67, 
                 I78, I89, PTr, years,PropTR)
l12<-QALYCostP(Q)
OWSAmat[12,1:2]<-l12
```

### High estimate
```{r}
Ch<-Bestparam[12]+Bestparam[12]*0.2
Q<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I8CD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mAIDS, mVIH235, mVIH35, mTr, 
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I55, 
                 I56, I67, 
                 I78, I89, PTr, years,PropTR)
h12<-QALYCostP(Q)
OWSAmat[12,3:4]<-h12
OWSAmat
Ch<-Bestparam[12]
```

## 13. Cl Partner change rate in low risk group
### Low estimate
```{r}
Cl<-Bestparam[13]-Bestparam[13]*0.2
Q<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I8CD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mAIDS, mVIH235, mVIH35, mTr, 
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I55, 
                 I56, I67, 
                 I78, I89, PTr, years,PropTR)
l13<-QALYCostP(Q)
OWSAmat[13,1:2]<-l13
```

### High estimate
```{r}
Cl<-Bestparam[13]+Bestparam[13]*0.2
Q<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I8CD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mAIDS, mVIH235, mVIH35, mTr, 
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I55, 
                 I56, I67, 
                 I78, I89, PTr, years,PropTR)
h13<-QALYCostP(Q)
OWSAmat[13,3:4]<-h13
OWSAmat
Cl<-Bestparam[13]
```

## 14. Cvl Partner change rate in very low risk group
### Low estimate
```{r}
Cvl<-Bestparam[14]-Bestparam[14]*0.2
Q<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I8CD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mAIDS, mVIH235, mVIH35, mTr, 
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I55, 
                 I56, I67, 
                 I78, I89, PTr, years, PropTR)
l14<-QALYCostP(Q)
OWSAmat[14,1:2]<-l14
```

### High estimate
```{r}
Cvl<-Bestparam[14]+Bestparam[14]*0.2
Q<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I8CD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mAIDS, mVIH235, mVIH35, mTr, 
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I55, 
                 I56, I67, 
                 I78, I89, PTr, years, PropTR)
h14<-QALYCostP(Q)
OWSAmat[14,3:4]<-h14
OWSAmat
Cvl<-Bestparam[14]
```

## 15. nvh proportion of the population in each group
### Low estimate
```{r}
nvh<-Bestparam[15]-Bestparam[15]*0.2
Q<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I8CD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mAIDS, mVIH235, mVIH35, mTr, 
                 Cvh, Ch, Cl, Cvl, 
                 nvh=Bestparam[15]-Bestparam[15]*0.2, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I55, 
                 I56, I67, 
                 I78, I89, PTr, years, PropTR)
l15<-QALYCostP(Q)
OWSAmat[15,1:2]<-l15
```

### High estimate
```{r}
nvh<-Bestparam[15]+Bestparam[15]*0.2
Q<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I8CD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mAIDS, mVIH235, mVIH35, mTr, 
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I55, 
                 I56, I67, 
                 I78, I89, PTr, years, PropTR)
h15<-QALYCostP(Q)
OWSAmat[15,3:4]<-h15
OWSAmat
nvh<-Bestparam[15]
```

## 16. nh proportion of the population in each group
### Low estimate
```{r}
nh<-Bestparam[16]-Bestparam[16]*0.2
Q<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I8CD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mAIDS, mVIH235, mVIH35, mTr, 
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I55, 
                 I56, I67, 
                 I78, I89, PTr, years, PropTR)
l16<-QALYCostP(Q)
OWSAmat[16,1:2]<-l16
```

### High estimate
```{r}
nh=Bestparam[16]+Bestparam[16]*0.2
Q<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I8CD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mAIDS, mVIH235, mVIH35, mTr, 
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I55, 
                 I56, I67, 
                 I78, I89, PTr, years, PropTR)
h16<-QALYCostP(Q)
OWSAmat[16,3:4]<-h16
OWSAmat
nh<-Bestparam[16]
```

## 17. nl proportion of the population in each group
### Low estimate
```{r}
nl<-Bestparam[17]-Bestparam[17]*0.2
Q<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I8CD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mAIDS, mVIH235, mVIH35, mTr, 
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I55, 
                 I56, I67, 
                 I78, I89, PTr, years, PropTR)
l17<-QALYCostP(Q)
OWSAmat[17,1:2]<-l17
```

### High estimate
```{r}
nl=Bestparam[17]+Bestparam[17]*0.2
Q<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I8CD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mAIDS, mVIH235, mVIH35, mTr, 
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl=Bestparam[17]+Bestparam[17]*0.2, nvl, B,
                 I12, I23, I34, 
                 I45, I55, 
                 I56, I67, 
                 I78, I89, PTr, years, PropTR)
h17<-QALYCostP(Q)
OWSAmat[17,3:4]<-h17
OWSAmat
nl<-Bestparam[17]
```

## 18. nvl proportion of the population in each group
### Low estimate
```{r}
nvl<-Bestparam[18]-Bestparam[18]*0.2
Q<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I8CD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mAIDS, mVIH235, mVIH35, mTr, 
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I55, 
                 I56, I67, 
                 I78, I89, PTr, years, PropTR)
l18<-QALYCostP(Q)
OWSAmat[18,1:2]<-l18
```

### High estimate
```{r}
nvl<-Bestparam[18]+Bestparam[18]*0.2
Q<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I8CD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mAIDS, mVIH235, mVIH35, mTr, 
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl=Bestparam[18]+Bestparam[18]*0.2, B,
                 I12, I23, I34, 
                 I45, I55, 
                 I56, I67, 
                 I78, I89, PTr, years, PropTR)
h18<-QALYCostP(Q)
OWSAmat[18,3:4]<-h18
OWSAmat
nvl<-Bestparam[18]
```

## 19. B per partnership transmissibility 
### Low estimate
```{r}
B<-Bestparam[19]-Bestparam[19]*0.2
Q<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I8CD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mAIDS, mVIH235, mVIH35, mTr, 
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B=Bestparam[19]-Bestparam[19]*0.2,
                 I12, I23, I34, 
                 I45, I55, 
                 I56, I67, 
                 I78, I89, PTr, years, PropTR)
l19<-QALYCostP(Q)
OWSAmat[19,1:2]<-l19
```

### High estimate
```{r}
B<-Bestparam[19]+Bestparam[19]*0.2
Q<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I8CD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mAIDS, mVIH235, mVIH35, mTr, 
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B=Bestparam[19]+Bestparam[19]*0.2,
                 I12, I23, I34, 
                 I45, I55, 
                 I56, I67, 
                 I78, I89, PTr, years, PropTR)
h19<-QALYCostP(Q)
OWSAmat[19,3:4]<-h19
OWSAmat
B<-Bestparam[19]
```

## 20. I12, 1 month duration in stage 1 of HIV infection
### Low estimate
```{r}
I12<-Bestparam[20]-Bestparam[20]*0.2
Q<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I8CD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mAIDS, mVIH235, mVIH35, mTr, 
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I55, 
                 I56, I67, 
                 I78, I89, PTr, years, PropTR)
l20<-QALYCostP(Q)
OWSAmat[20,1:2]<-l20
```

### High estimate
```{r}
I12<-Bestparam[20]+Bestparam[20]*0.2
Q<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I8CD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mAIDS, mVIH235, mVIH35, mTr, 
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I55, 
                 I56, I67, 
                 I78, I89, PTr, years, PropTR)
h20<-QALYCostP(Q)
OWSAmat[20,3:4]<-h20
OWSAmat
I12<-Bestparam[20]
```

## 21. I23, 1 month duration in stage 2 of HIV infection
### Low estimate
```{r}
I23<-Bestparam[21]-Bestparam[21]*0.2
Q<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I8CD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mAIDS, mVIH235, mVIH35, mTr, 
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I55, 
                 I56, I67, 
                 I78, I89, PTr, years, PropTR)
l21<-QALYCostP(Q)
OWSAmat[21,1:2]<-l21
```

### High estimate
```{r}
I23<-Bestparam[21]+Bestparam[21]*0.2
Q<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I8CD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mAIDS, mVIH235, mVIH35, mTr, 
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I55, 
                 I56, I67, 
                 I78, I89, PTr, years, PropTR)
h21<-QALYCostP(Q)
OWSAmat[21,3:4]<-h21
OWSAmat
I23<-Bestparam[21]
```

## 22. I34, 1 month duration in stage 3 of HIV infection
### Low estimate
```{r}
I34<-Bestparam[22]-Bestparam[22]*0.2
Q<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I8CD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mAIDS, mVIH235, mVIH35, mTr, 
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I55, 
                 I56, I67, 
                 I78, I89, PTr, years, PropTR)
l22<-QALYCostP(Q)
OWSAmat[22,1:2]<-l22
```

### High estimate
```{r}
I34<-Bestparam[22]+Bestparam[22]*0.2
Q<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I8CD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mAIDS, mVIH235, mVIH35, mTr, 
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I55, 
                 I56, I67, 
                 I78, I89, PTr, years, PropTR)
h22<-QALYCostP(Q)
OWSAmat[22,3:4]<-h22
OWSAmat
I34<-Bestparam[22]
```

## 23. I45, 3 month duration in stage 4 of HIV infection
### Low estimate
```{r}
I45<-Bestparam[23]-Bestparam[23]*0.2
Q<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I8CD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mAIDS, mVIH235, mVIH35, mTr, 
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I55, 
                 I56, I67, 
                 I78, I89, PTr, years, PropTR)
l23<-QALYCostP(Q)
OWSAmat[23,1:2]<-l23
```

### High estimate
```{r}
I45=Bestparam[23]+Bestparam[23]*0.2
Q<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I8CD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mAIDS, mVIH235, mVIH35, mTr, 
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I55, 
                 I56, I67, 
                 I78, I89, PTr, years, PropTR)
h23<-QALYCostP(Q)
OWSAmat[23,3:4]<-h23
OWSAmat
I45<-Bestparam[23]
```

## 26. I56, 3 month duration in stage 5 of HIV infection
### Low estimate
```{r}
I56<-Bestparam[26]-Bestparam[26]*0.2
Q<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I8CD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mAIDS, mVIH235, mVIH35, mTr, 
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I55, 
                 I56, I67, 
                 I78, I89, PTr, years, PropTR)
l26<-QALYCostP(Q)
OWSAmat[24,1:2]<-l26
```

### High estimate
```{r}
I56<-Bestparam[26]+Bestparam[26]*0.2
Q<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I8CD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mAIDS, mVIH235, mVIH35, mTr, 
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I55, 
                 I56, I67, 
                 I78, I89, PTr, years, PropTR)
h26<-QALYCostP(Q)
OWSAmat[24,3:4]<-h26
OWSAmat
I56<-Bestparam[26]
```

## 27. I67, 3 month duration in stage 6 of HIV infection
### Low estimate
```{r}
I67<-Bestparam[27]-Bestparam[27]*0.2
Q<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I8CD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mAIDS, mVIH235, mVIH35, mTr, 
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I55, 
                 I56, I67, 
                 I78, I89, PTr, years, PropTR)
l27<-QALYCostP(Q)
OWSAmat[25,1:2]<-l27
```

### High estimate
```{r}
I67<-Bestparam[27]+Bestparam[27]*0.2
Q<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I8CD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mAIDS, mVIH235, mVIH35, mTr, 
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I55, 
                 I56, I67, 
                 I78, I89, PTr, years, PropTR)
h27<-QALYCostP(Q)
OWSAmat[25,3:4]<-h27
OWSAmat
I67<-Bestparam[27]
```

## 28. I78, Chronic duration in stage 7
### Low estimate
```{r}
I78<-Bestparam[28]-Bestparam[28]*0.2
Q<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I8CD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mAIDS, mVIH235, mVIH35, mTr, 
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I55, 
                 I56, I67, 
                 I78, I89, PTr, years, PropTR)
l28<-QALYCostP(Q)
OWSAmat[26,1:2]<-l28
```

### High estimate
```{r}
I78<-Bestparam[28]+Bestparam[28]*0.2
Q<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I8CD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mAIDS, mVIH235, mVIH35, mTr, 
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I55, 
                 I56, I67, 
                 I78, I89, PTr, years, PropTR)
h28<-QALYCostP(Q)
OWSAmat[26,3:4]<-h28
OWSAmat
I78<-Bestparam[28]
```

## 29. I89, chronic duration in stage 9 of HIV infection
### Low estimate
```{r}
I89<-Bestparam[29]-Bestparam[29]*0.2
Q<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I8CD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mAIDS, mVIH235, mVIH35, mTr, 
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I55, 
                 I56, I67, 
                 I78, I89, PTr, years, PropTR)
l29<-QALYCostP(Q)
OWSAmat[27,1:2]<-l29
```

### High estimate
```{r}
I89<-Bestparam[29]+Bestparam[29]*0.2
Q<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I8CD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mAIDS, mVIH235, mVIH35, mTr, 
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I55, 
                 I56, I67, 
                 I78, I89, PTr, years, PropTR)
h29<-QALYCostP(Q)
OWSAmat[27,3:4]<-h29
OWSAmat
I89<-Bestparam[29]
```

## 30. PTr[1], Probaility of starting treatment
### Low estimate
```{r}
PTr<-c(Bestparam[30]-Bestparam[30]*0.2,Bestparam[31],Bestparam[32])
Q<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I8CD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mAIDS, mVIH235, mVIH35, mTr, 
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I55, 
                 I56, I67, 
                 I78, I89, PTr, years, PropTR)
l30<-QALYCostP(Q)
OWSAmat[28,1:2]<-l30
```

### High estimate
```{r}
PTr<-c(Bestparam[30]+Bestparam[30]*0.2,Bestparam[31],Bestparam[32])
Q<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I8CD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mAIDS, mVIH235, mVIH35, mTr, 
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I55, 
                 I56, I67, 
                 I78, I89, PTr=c(Bestparam[30]+Bestparam[30]*0.2,Bestparam[31],Bestparam[32]), years, PropTR)
h30<-QALYCostP(Q)
OWSAmat[28,3:4]<-h30
OWSAmat
PTr<-c(Bestparam[30],Bestparam[31],Bestparam[32])
```


## 31. PTr[2], Probaility of starting treatment
### Low estimate
```{r}
PTr<-c(Bestparam[30],Bestparam[31]-Bestparam[31]*0.2,Bestparam[32])
Q<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I8CD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mAIDS, mVIH235, mVIH35, mTr, 
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I55, 
                 I56, I67, 
                 I78, I89, PTr, years, PropTR)
l31<-QALYCostP(Q)
OWSAmat[29,1:2]<-l31
```

### High estimate
```{r}
PTr<-c(Bestparam[30],Bestparam[31]+Bestparam[31]*0.2,Bestparam[32])
Q<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I8CD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mAIDS, mVIH235, mVIH35, mTr, 
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I55, 
                 I56, I67, 
                 I78, I89, PTr, years, PropTR)
h31<-QALYCostP(Q)
OWSAmat[29,3:4]<-h31
OWSAmat
PTr<-c(Bestparam[30],Bestparam[31],Bestparam[32])
```

## 32. PTr[3], Probaility of starting treatment
### Low estimate
```{r}
PTr<-c(Bestparam[30],Bestparam[31],Bestparam[32]-Bestparam[32]*0.2)
Q<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I8CD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mAIDS, mVIH235, mVIH35, mTr, 
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I55, 
                 I56, I67, 
                 I78, I89, PTr, years, PropTR)
l32<-QALYCostP(Q)
OWSAmat[30,1:2]<-l32
```

### High estimate
```{r}
PTr<-c(Bestparam[30],Bestparam[31],Bestparam[32]+Bestparam[32]*0.2)
Q<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I8CD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mAIDS, mVIH235, mVIH35, mTr, 
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I55, 
                 I56, I67, 
                 I78, I89, PTr, years, PropTR)
h32<-QALYCostP(Q)
OWSAmat[30,3:4]<-h32
OWSAmat
PTr<-c(Bestparam[30],Bestparam[31],Bestparam[32])
```
## Impacto de la adherencia
### High estimate & Low estimate
```{r}
Q<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I8CD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mAIDS, mVIH235, mVIH35, mTr, 
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I55, 
                 I56, I67, 
                 I78, I89, PTr, years, PropTR)
h_l33<-QALYCostP(Q)
OWSAmat[31,1:2]<-h_l33
OWSAmat[31,3:4]<-h_l33
OWSAmat
```
############################################################################################################-------Análisis OWA PrEP LCA----------############################################
#############################################################################################
```{r}
source("HIVSIM04.R")
source("QALYCostP.R")
Woff<-1-exp(-0.12/52)
W<-1-exp(-0.3/52)
PrEPcost<-390 
RiskRed<-1-0.96 
OWSAmatP<-matrix(ncol=4, nrow=31, dimnames=list(NULL, c("QALYslP", "CostslP", "QALYshP", "CostshP")))
```




## 1. NumHSHVIH
### Low estimate
```{r}
NumHSHVIH<-Bestparam[1]-Bestparam[1]*0.2
NumHSH<-892955-NumHSHVIH 

QP<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I8CD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mAIDS, mVIH235, mVIH35, mTr, 
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I55, 
                 I56, I67, 
                 I78, I89, PTr, years)

l1P<-QALYCostP(QP)
l1P
OWSAmatP[1,1:2]<-l1P
OWSAmatP
```

### High estimate
```{r}
NumHSHVIH<-Bestparam[1]-Bestparam[1]*0.2
NumHSH<-892955-NumHSHVIH 
QP<-HIVSIMPREP(Age, NoSem, NumHSH=892955-NumHSHVIH, NumHSHVIH, 
                 ACD4, I8CD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mAIDS, mVIH235, mVIH35, mTr, 
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I55, 
                 I56, I67, 
                 I78, I89, PTr, years)

h1P<-QALYCostP(QP)
h1P
OWSAmatP[1,3:4]<-h1P
OWSAmatP
NumHSHVIH<-Bestparam[1]
NumHSH<-892955-NumHSHVIH 
```

## 2. % pacientes con CD4 menor de 200
### Low estimate
```{r}
ACD4<-Bestparam[2]-Bestparam[2]*0.2
QP<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I8CD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mAIDS, mVIH235, mVIH35, mTr, 
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I55, 
                 I56, I67, 
                 I78, I89, PTr, years)
l2P<-QALYCostP(QP)
OWSAmatP[2,1:2]<-l2P
```

### High estimate
```{r}
ACD4<-Bestparam[2]+Bestparam[2]*0.2

QP<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I8CD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mAIDS, mVIH235, mVIH35, mTr, 
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I55, 
                 I56, I67, 
                 I78, I89, PTr, years)

h2P<-QALYCostP(QP)
OWSAmatP[2,3:4]<-h2P
OWSAmatP
ACD4<-Bestparam[2]
```

## 3. % pacientes con CD4 entre 200-350
### Low estimate
```{r}
I8CD4<-Bestparam[3]-Bestparam[3]*0.2
QP<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I8CD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mAIDS, mVIH235, mVIH35, mTr, 
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I55, 
                 I56, I67, 
                 I78, I89, PTr, years)
l3P<-QALYCostP(QP)
OWSAmatP[3,1:2]<-l3P
```

### High estimate
```{r}
I8CD4<-Bestparam[3]+Bestparam[3]*0.2
QP<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I8CD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mAIDS, mVIH235, mVIH35, mTr, 
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I55, 
                 I56, I67, 
                 I78, I89, PTr, years)


h3P<-QALYCostP(QP)
OWSAmatP[3,3:4]<-h3P
OWSAmatP
I8CD4<-Bestparam[3]
```

## 4. % pacientes con CD4 entre 350-500
### Low estimate
```{r}
I7CD4<-Bestparam[4]-Bestparam[4]*0.2
QP<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I8CD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mAIDS, mVIH235, mVIH35, mTr, 
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I55, 
                 I56, I67, 
                 I78, I89, PTr, years)
l4P<-QALYCostP(QP)
OWSAmatP[4,1:2]<-l4P
```

### High estimate
```{r}
I7CD4=Bestparam[4]+Bestparam[4]*0.2
QP<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I8CD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mAIDS, mVIH235, mVIH35, mTr, 
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I55, 
                 I56, I67, 
                 I78, I89, PTr, years)

h4P<-QALYCostP(QP)
OWSAmatP[4,3:4]<-h4P
OWSAmatP
I7CD4<-Bestparam[4]
```

## 5. % pacientes con CD4 mayor de 500
### Low estimate
```{r}
Rest<-Bestparam[5]-Bestparam[5]*0.2
QP<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I8CD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mAIDS, mVIH235, mVIH35, mTr, 
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I55, 
                 I56, I67, 
                 I78, I89, PTr, years)
l5P<-QALYCostP(QP)
OWSAmatP[5,1:2]<-l5P
```

### High estimate
```{r}
Rest<-Bestparam[5]+Bestparam[5]*0.2
QP<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I8CD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mAIDS, mVIH235, mVIH35, mTr, 
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I55, 
                 I56, I67, 
                 I78, I89, PTr, years)

h5P<-QALYCostP(QP)
OWSAmatP[5,3:4]<-h5P
OWSAmatP
Rest<-Bestparam[5]
```
## 6. Proportion on treatment
### Low estimate
```{r}
PropTR<-Bestparam[6]-Bestparam[6]*0.2
QP<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I8CD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mAIDS, mVIH235, mVIH35, mTr, 
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I55, 
                 I56, I67, 
                 I78, I89, PTr, years, PropTR)
l6P<-QALYCostP(QP)
OWSAmatP[6,1:2]<-l6P
```

### High estimate
```{r}
PropTR<-Bestparam[6]+Bestparam[6]*0.2
QP<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I8CD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mAIDS, mVIH235, mVIH35, mTr, 
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I55, 
                 I56, I67, 
                 I78, I89, PTr, years, PropTR)
h6P<-QALYCostP(QP)
OWSAmatP[6,3:4]<-h6P
OWSAmatP
PropTR<-Bestparam[6]
```

## 7. Proportion on treatment at start
### Low estimate
```{r}
G<-Bestparam[7]-Bestparam[7]*0.2
QP<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I8CD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mAIDS, mVIH235, mVIH35, mTr, 
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I55, 
                 I56, I67, 
                 I78, I89, PTr, years,PropTR)
l7P<-QALYCostP(QP)
OWSAmatP[7,1:2]<-l7P
```

### High estimate
```{r}
G<-Bestparam[7]+Bestparam[7]*0.2
QP<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I8CD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mAIDS, mVIH235, mVIH35, mTr, 
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I55, 
                 I56, I67, 
                 I78, I89, PTr, years,PropTR)
h7P<-QALYCostP(QP)
OWSAmatP[7,3:4]<-h7P
OWSAmatP
G<-Bestparam[7]
```

## 8. Mortality HIV 200-350 CD4
### Low estimate
```{r}
mVIH235<-Bestparam[8]-Bestparam[8]*0.2
QP<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I8CD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mAIDS, mVIH235, mVIH35, 
                 mTr, 
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I55, 
                 I56, I67, 
                 I78, I89, PTr, years,PropTR)
l8P<-QALYCostP(QP)
OWSAmatP[8,1:2]<-l8P
```

### High estimate
```{r}
mVIH235<-Bestparam[8]+Bestparam[8]*0.2
QP<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I8CD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mAIDS, mVIH235, mVIH35, 
                 mTr, 
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I55, 
                 I56, I67, 
                 I78, I89, PTr, years,PropTR)
h8P<-QALYCostP(QP)
OWSAmatP[8,3:4]<-h8P
OWSAmatP
mVIH235<-Bestparam[8]
```

## 9. Mortality HIV >350 CD4
### Low estimate
```{r}
mVIH35<-Bestparam[9]-Bestparam[9]*0.2
QP<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I8CD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mAIDS, mVIH235, mVIH35, 
                 mTr, 
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I55, 
                 I56, I67, 
                 I78, I89, PTr, years,PropTR)
l9P<-QALYCostP(QP)
OWSAmatP[9,1:2]<-l9P
```

### High estimate
```{r}
mVIH35<-Bestparam[9]+Bestparam[9]*0.2
QP<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I8CD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mAIDS, mVIH235, mVIH35, 
                 mTr, 
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I55, 
                 I56, I67, 
                 I78, I89, PTr, years,PropTR)
h9P<-QALYCostP(QP)
OWSAmatP[9,3:4]<-h9P
OWSAmatP
mVIH35<-Bestparam[9]
```

## 10. Mortality AIDS
### Low estimate
```{r}
mAIDS<-Bestparam[10]-Bestparam[10]*0.2
QP<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I8CD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mAIDS, mVIH235,  
                 mVIH35, mTr, 
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I55, 
                 I56, I67, 
                 I78, I89, PTr, years,PropTR)
l10P<-QALYCostP(QP)
OWSAmatP[10,1:2]<-l10P
```

### High estimate
```{r}
mAIDS<-Bestparam[10]+Bestparam[10]*0.2
QP<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I8CD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mAIDS, mVIH235, mVIH35,
                 mTr, 
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I55, 
                 I56, I67, 
                 I78, I89, PTr, years,PropTR)
h10P<-QALYCostP(QP)
OWSAmatP[10,3:4]<-h10P
OWSAmatP
mAIDS<-Bestparam[10]
```

## 11. Cvh Partner change rate in very hig risk group
### Low estimate
```{r}
Cvh<-Bestparam[11]-Bestparam[11]*0.2
QP<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I8CD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mAIDS, mVIH235, mVIH35, mTr, 
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I55, 
                 I56, I67, 
                 I78, I89, PTr, years,PropTR)
l11P<-QALYCostP(QP)
OWSAmatP[11,1:2]<-l11P
```

### High estimate
```{r}
Cvh<-Bestparam[11]+Bestparam[11]*0.2
QP<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I8CD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mAIDS, mVIH235, mVIH35, mTr, 
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I55, 
                 I56, I67, 
                 I78, I89, PTr, years,PropTR)
h11P<-QALYCostP(QP)
OWSAmatP[11,3:4]<-h11P
OWSAmatP
Cvh<-Bestparam[11]
```

## 12. Ch Partner change rate in high risk group
### Low estimate
```{r}
Ch<-Bestparam[12]-Bestparam[12]*0.2
QP<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I8CD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mAIDS, mVIH235, mVIH35, mTr, 
                 Cvh, Ch=Bestparam[12]-Bestparam[12]*0.2, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I55, 
                 I56, I67, 
                 I78, I89, PTr, years,PropTR)
l12P<-QALYCostP(QP)
OWSAmatP[12,1:2]<-l12P
```

### High estimate
```{r}
Ch<-Bestparam[12]+Bestparam[12]*0.2
QP<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I8CD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mAIDS, mVIH235, mVIH35, mTr, 
                 Cvh, Ch=Bestparam[12]+Bestparam[12]*0.2, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I55, 
                 I56, I67, 
                 I78, I89, PTr, years,PropTR)
h12P<-QALYCostP(QP)
OWSAmatP[12,3:4]<-h12P
OWSAmatP
Ch<-Bestparam[12]
```

## 13. Cl Partner change rate in low risk group
### Low estimate
```{r}
Cl<-Bestparam[13]-Bestparam[13]*0.2
QP<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I8CD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mAIDS, mVIH235, mVIH35, mTr, 
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I55, 
                 I56, I67, 
                 I78, I89, PTr, years,PropTR)
l13P<-QALYCostP(QP)
OWSAmatP[13,1:2]<-l13P
```

### High estimate
```{r}
Cl<-Bestparam[13]+Bestparam[13]*0.2
QP<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I8CD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mAIDS, mVIH235, mVIH35, mTr, 
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I55, 
                 I56, I67, 
                 I78, I89, PTr, years,PropTR)
h13P<-QALYCostP(QP)
OWSAmatP[13,3:4]<-h13P
OWSAmatP
Cl<-Bestparam[13]
```

## 14. Cvl Partner change rate in very low risk group
### Low estimate
```{r}
Cvl<-Bestparam[14]-Bestparam[14]*0.2
QP<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I8CD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mAIDS, mVIH235, mVIH35, mTr, 
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I55, 
                 I56, I67, 
                 I78, I89, PTr, years, PropTR)
l14P<-QALYCostP(QP)
OWSAmatP[14,1:2]<-l14P
```

### High estimate
```{r}
Cvl<-Bestparam[14]+Bestparam[14]*0.2
QP<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I8CD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mAIDS, mVIH235, mVIH35, mTr, 
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I55, 
                 I56, I67, 
                 I78, I89, PTr, years, PropTR)
h14P<-QALYCostP(QP)
OWSAmatP[14,3:4]<-h14P
OWSAmatP
Cvl<-Bestparam[14]
```

## 15. nvh proportion of the population in each group
### Low estimate
```{r}
nvh<-Bestparam[15]-Bestparam[15]*0.2
QP<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I8CD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mAIDS, mVIH235, mVIH35, mTr, 
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I55, 
                 I56, I67, 
                 I78, I89, PTr, years, PropTR)
l15P<-QALYCostP(QP)
OWSAmatP[15,1:2]<-l15P
```

### High estimate
```{r}
nvh<-Bestparam[15]+Bestparam[15]*0.2
QP<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I8CD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mAIDS, mVIH235, mVIH35, mTr, 
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I55, 
                 I56, I67, 
                 I78, I89, PTr, years, PropTR)
h15P<-QALYCostP(QP)
OWSAmatP[15,3:4]<-h15P
OWSAmatP
nvh<-Bestparam[15]
```

## 16. nh proportion of the population in each group
### Low estimate
```{r}
nh<-Bestparam[16]-Bestparam[16]*0.2
QP<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I8CD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mAIDS, mVIH235, mVIH35, mTr, 
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I55, 
                 I56, I67, 
                 I78, I89, PTr, years, PropTR)
l16P<-QALYCostP(QP)
OWSAmatP[16,1:2]<-l16P
```

### High estimate
```{r}
nh<-Bestparam[16]+Bestparam[16]*0.2
QP<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I8CD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mAIDS, mVIH235, mVIH35, mTr, 
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I55, 
                 I56, I67, 
                 I78, I89, PTr, years, PropTR)
h16P<-QALYCostP(QP)
OWSAmatP[16,3:4]<-h16P
OWSAmatP
nh<-Bestparam[16]
```

## 17. nl proportion of the population in each group
### Low estimate
```{r}
nl<-Bestparam[17]-Bestparam[17]*0.2
QP<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I8CD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mAIDS, mVIH235, mVIH35, mTr, 
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I55, 
                 I56, I67, 
                 I78, I89, PTr, years, PropTR)
l17P<-QALYCostP(QP)
OWSAmatP[17, 1:2]<-l17P
```

### High estimate
```{r}
nl<-Bestparam[17]+Bestparam[17]*0.2
QP<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I8CD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mAIDS, mVIH235, mVIH35, mTr, 
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I55, 
                 I56, I67, 
                 I78, I89, PTr, years, PropTR)
h17P<-QALYCostP(QP)
OWSAmatP[17,3:4]<-h17P
OWSAmatP
nl<-Bestparam[17]
```

## 18. nvl proportion of the population in each group
### Low estimate
```{r}
nvl<-Bestparam[18]-Bestparam[18]*0.2
QP<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I8CD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mAIDS, mVIH235, mVIH35, mTr, 
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I55, 
                 I56, I67, 
                 I78, I89, PTr, years, PropTR)
l18P<-QALYCostP(QP)
OWSAmatP[18, 1:2]<-l18P
```

### High estimate
```{r}
nvl<-Bestparam[18]+Bestparam[18]*0.2
QP<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I8CD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mAIDS, mVIH235, mVIH35, mTr, 
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I55, 
                 I56, I67, 
                 I78, I89, PTr, years, PropTR)
h18P<-QALYCostP(QP)
OWSAmatP[18,3:4]<-h18P
OWSAmatP
nvl<-Bestparam[18]
```

## 19. B per partnership transmissibility 
### Low estimate
```{r}
B<-Bestparam[19]-Bestparam[19]*0.2
QP<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I8CD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mAIDS, mVIH235, mVIH35, mTr, 
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I55, 
                 I56, I67, 
                 I78, I89, PTr, years, PropTR)
l19P<-QALYCostP(QP)
OWSAmatP[19, 1:2]<-l19P
```

### High estimate
```{r}
B<-Bestparam[19]+Bestparam[19]*0.2
QP<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I8CD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mAIDS, mVIH235, mVIH35, mTr, 
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I55, 
                 I56, I67, 
                 I78, I89, PTr, years, PropTR)
h19P<-QALYCostP(QP)
OWSAmatP[19,3:4]<-h19P
OWSAmatP
B<-Bestparam[19]
```

## 20. I12, 1 month duration in stage 1 of HIV infection
### Low estimate
```{r}
I12<-Bestparam[20]-Bestparam[20]*0.2
QP<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I8CD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mAIDS, mVIH235, mVIH35, mTr, 
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I55, 
                 I56, I67, 
                 I78, I89, PTr, years, PropTR)
l20P<-QALYCostP(QP)
OWSAmatP[20, 1:2]<-l20P
```

### High estimate
```{r}
I12<-Bestparam[20]+Bestparam[20]*0.2
QP<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I8CD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mAIDS, mVIH235, mVIH35, mTr, 
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I55, 
                 I56, I67, 
                 I78, I89, PTr, years, PropTR)
h20P<-QALYCostP(QP)
OWSAmatP[20,3:4]<-h20P
OWSAmatP
I12<-Bestparam[20]
```

## 21. I23, 1 month duration in stage 2 of HIV infection
### Low estimate
```{r}
I23<-Bestparam[21]-Bestparam[21]*0.2
QP<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I8CD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mAIDS, mVIH235, mVIH35, mTr, 
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I55, 
                 I56, I67, 
                 I78, I89, PTr, years, PropTR)
l21P<-QALYCostP(QP)
OWSAmatP[21, 1:2]<-l21P
```

### High estimate
```{r}
I23<-Bestparam[21]+Bestparam[21]*0.2
QP<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I8CD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mAIDS, mVIH235, mVIH35, mTr, 
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23=Bestparam[21]+Bestparam[21]*0.2, I34, 
                 I45, I55, 
                 I56, I67, 
                 I78, I89, PTr, years, PropTR)
h21P<-QALYCostP(QP)
OWSAmatP[21,3:4]<-h21P
OWSAmatP
I23<-Bestparam[21]
```

## 22. I34, 1 month duration in stage 3 of HIV infection
### Low estimate
```{r}
I34<-Bestparam[22]-Bestparam[22]*0.2
QP<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I8CD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mAIDS, mVIH235, mVIH35, mTr, 
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34=Bestparam[22]-Bestparam[22]*0.2, 
                 I45, I55, 
                 I56, I67, 
                 I78, I89, PTr, years, PropTR)
l22P<-QALYCostP(QP)
OWSAmatP[22, 1:2]<-l22P
```

### High estimate
```{r}
I34<-Bestparam[22]+Bestparam[22]*0.2
QP<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I8CD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mAIDS, mVIH235, mVIH35, mTr, 
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I55, 
                 I56, I67, 
                 I78, I89, PTr, years, PropTR)
h22P<-QALYCostP(QP)
OWSAmatP[22,3:4]<-h22P
OWSAmatP
I34<-Bestparam[22]
```

## 23. I45, 3 month duration in stage 4 of HIV infection
### Low estimate
```{r}
I45<-Bestparam[23]-Bestparam[23]*0.2
QP<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I8CD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mAIDS, mVIH235, mVIH35, mTr, 
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I55, 
                 I56, I67, 
                 I78, I89, PTr, years, PropTR)
l23P<-QALYCostP(QP)
OWSAmatP[23, 1:2]<-l23P
```

### High estimate
```{r}
I45<-Bestparam[23]+Bestparam[23]*0.2
QP<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I8CD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mAIDS, mVIH235, mVIH35, mTr, 
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I55, 
                 I56, I67, 
                 I78, I89, PTr, years, PropTR)
h23P<-QALYCostP(QP)
OWSAmatP[23,3:4]<-h23P
OWSAmatP
I45<-Bestparam[23]
```

## 26. I56, 3 month duration in stage 5 of HIV infection
### Low estimate
```{r}
I56<-Bestparam[26]-Bestparam[26]*0.2
QP<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I8CD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mAIDS, mVIH235, mVIH35, mTr, 
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I55, 
                 I56, I67, 
                 I78, I89, PTr, years, PropTR)
l26P<-QALYCostP(QP)
OWSAmatP[24, 1:2]<-l26P
```

### High estimate
```{r}
I56<-Bestparam[26]+Bestparam[26]*0.2
QP<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I8CD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mAIDS, mVIH235, mVIH35, mTr, 
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I55, 
                 I56, I67, 
                 I78, I89, PTr, years, PropTR)
h26P<-QALYCostP(QP)
OWSAmatP[24,3:4]<-h26P
OWSAmatP
I56<-Bestparam[26]
```

## 27. I67, 3 month duration in stage 6 of HIV infection
### Low estimate
```{r}
I67<-Bestparam[27]-Bestparam[27]*0.2
QP<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I8CD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mAIDS, mVIH235, mVIH35, mTr, 
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I55, 
                 I56, I67, 
                 I78, I89, PTr, years, PropTR)
l27P<-QALYCostP(QP)
OWSAmatP[25, 1:2]<-l27P
```

### High estimate
```{r}
I67<-Bestparam[27]+Bestparam[27]*0.2
QP<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I8CD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mAIDS, mVIH235, mVIH35, mTr, 
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I55, 
                 I56, I67=Bestparam[27]+Bestparam[27]*0.2, 
                 I78, I89, PTr, years, PropTR)
h27P<-QALYCostP(QP)
OWSAmatP[25,3:4]<-h27P
OWSAmatP
I67<-Bestparam[27]
```

## 28. I78, Chronic duration in stage 7
### Low estimate
```{r}
I78=Bestparam[28]-Bestparam[28]*0.2
QP<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I8CD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mAIDS, mVIH235, mVIH35, mTr, 
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I55, 
                 I56, I67, 
                 I78, I89, PTr, years, PropTR)
  l28P<-QALYCostP(QP)
OWSAmatP[26, 1:2]<-l28P
```

### High estimate
```{r}
I78<-Bestparam[28]+Bestparam[28]*0.2
QP<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I8CD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mAIDS, mVIH235, mVIH35, mTr, 
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I55, 
                 I56, I67, 
                 I78, I89, PTr, years, PropTR)
h28P<-QALYCostP(QP)
OWSAmatP[26,3:4]<-h28P
OWSAmatP
I78<-Bestparam[28]
```

## 29. I89, chronic duration in stage 9 of HIV infection
### Low estimate
```{r}
I89<-Bestparam[29]-Bestparam[29]*0.2
QP<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I8CD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mAIDS, mVIH235, mVIH35, mTr, 
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I55, 
                 I56, I67, 
                 I78, I89, PTr, years, PropTR)
l29P<-QALYCostP(QP)
OWSAmatP[27, 1:2]<-l29P
```

### High estimate
```{r}
I89<-Bestparam[29]+Bestparam[29]*0.2
QP<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I8CD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mAIDS, mVIH235, mVIH35, mTr, 
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I55, 
                 I56, I67, 
                 I78, I89, PTr, years, PropTR)
h29P<-QALYCostP(QP)
OWSAmatP[27,3:4]<-h29P
OWSAmatP
I89<-Bestparam[29]
```

## 30. PTr[1], Probaility of starting treatment
### Low estimate
```{r}
PTr<-c(Bestparam[30]-Bestparam[30]*0.2,Bestparam[31],Bestparam[32])
QP<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I8CD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mAIDS, mVIH235, mVIH35, mTr, 
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I55, 
                 I56, I67, 
                 I78, I89, PTr, years, PropTR)
l30P<-QALYCostP(QP)
OWSAmatP[28, 1:2]<-l30P
```

### High estimate
```{r}
PTr<-c(Bestparam[30]+Bestparam[30]*0.2,Bestparam[31],Bestparam[32])
QP<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I8CD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mAIDS, mVIH235, mVIH35, mTr, 
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I55, 
                 I56, I67, 
                 I78, I89, PTr, years, PropTR)
h30P<-QALYCostP(QP)
OWSAmatP[28,3:4]<-h30P
OWSAmatP
PTr<-c(Bestparam[30],Bestparam[31],Bestparam[32])
```

## 31. PTr[2], Probaility of starting treatment
### Low estimate
```{r}
PTr<-c(Bestparam[30],Bestparam[31]-Bestparam[31]*0.2,Bestparam[32])
QP<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I8CD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mAIDS, mVIH235, mVIH35, mTr, 
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I55, 
                 I56, I67, 
                 I78, I89, PTr, years, PropTR)
l31P<-QALYCostP(QP)
OWSAmatP[29, 1:2]<-l31P
```

### High estimate
```{r}
PTr<-c(Bestparam[30],Bestparam[31]+Bestparam[31]*0.2,Bestparam[32])
QP<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I8CD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mAIDS, mVIH235, mVIH35, mTr, 
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I55, 
                 I56, I67, 
                 I78, I89, PTr, years, PropTR)
h31P<-QALYCostP(QP)
OWSAmatP[29,3:4]<-h31P
OWSAmatP
PTr<-c(Bestparam[30],Bestparam[31],Bestparam[32])
```

## 32. PTr[3], Probaility of starting treatment
### Low estimate
```{r}
PTr<-c(Bestparam[30],Bestparam[31],Bestparam[32]+Bestparam[32]*0.2)
QP<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I8CD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mAIDS, mVIH235, mVIH35, mTr, 
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I55, 
                 I56, I67, 
                 I78, I89, PTr, years, PropTR)
l32P<-QALYCostP(QP)
OWSAmatP[30, 1:2]<-l32P
```

### High estimate
```{r}
PTr<-c(Bestparam[30],Bestparam[31],Bestparam[32]+Bestparam[32]*0.2)
QP<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I8CD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mAIDS, mVIH235, mVIH35, mTr, 
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I55, 
                 I56, I67, 
                 I78, I89, PTr, years, PropTR)
h32P<-QALYCostP(QP)
OWSAmatP[30,3:4]<-h32P
OWSAmatP
PTr<-c(Bestparam[30],Bestparam[31],Bestparam[32])
```
## Impacto de la adherencia
### High estimate
```{r}
RiskRed<-(1-0.96)*1
QP<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I8CD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mAIDS, mVIH235, mVIH35, mTr, 
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I55, 
                 I56, I67, 
                 I78, I89, PTr, years, PropTR)
h33<-QALYCostP(QP)
OWSAmatP[31,1:2]<-h33
OWSAmatP
```
### Low estimate
```{r}
RiskRed<-(1-0.96)*0.7
QP<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I8CD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mAIDS, mVIH235, mVIH35, mTr, 
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I55, 
                 I56, I67, 
                 I78, I89, PTr, years, PropTR)
l33<-QALYCostP(QP)
OWSAmatP[31,3:4]<-l33
OWSAmatP
```


# Combine, save and export
```{r}
save(OWSAmat, file="OWSAmat_TDF")
save(OWSAmatP, file="OWSAmat_LCA")
load("OWSAmat_TDF")
load("OWSAmat_LCA")

OWSADAT<-cbind(OWSAmat, OWSAmatP)
save(OWSADAT, file="OWSADAT_TDF_LCA")
head(OWSADAT)
```

```{r}
ICER_Low<-(OWSADAT[,6]-OWSADAT[,2])/(OWSADAT[,5]-OWSADAT[,1])
ICER_High<-(OWSADAT[,8]-OWSADAT[,4])/(OWSADAT[,7]-OWSADAT[,3])
ICER_High
ICER_Low
Variable<-c("HIV-MSM", "ACD4", "I8CD4", "I7CD4", "Rest", "G","PropTR","mVIH235","mVIH35","mAIDS","Cvh","Ch","Cl","Cvl","nvh","nh","nl","nvl",
"B","I12","I23","I34","I45","I56","I67","I78", "I89","PTr1", "PTr2", "PTr3", "Adherence")
ICER<-77800
ICERS<-NULL
ICERS<-data.frame(Variable, ICER_High, ICER_Low, ICER)
ICERS$dif<-abs(ICERS$ICER_High-ICERS$ICER_Low)


OWSATDFLCA<-ICERS %>%
  mutate(Variable = fct_reorder(Variable, dif)) %>%
  ggplot(aes(y=ICER,
            x=Variable, 
            ymin=ICERS[,2], ymax=ICERS[,3]))+     
  geom_linerange(size=5)+
  coord_flip()+
  theme(plot.margin=unit(c(1,1,1,1), "cm"))+
  #geom_hline(yintercept=79613.82 , col="blue" )+
  geom_hline(yintercept=33895.59, col="red" )+
  ylab("ICER")+
  theme_classic()
#tiff("OWSATDF_LCA_01.tif", width=16, height=12, units="cm", res=300)
OWSATDFLCA
#save(OWSATDF, file="OWSATDF_LCA")
#dev.off

```