---
title: "Coste-eficacia de PrEP en España"
author: "Philip Wikman"
date: "15 de mayo de 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(dplyr)
library(forcats)
source("R/QALYCostP.R")
source("HIVSIM05.R")
source("R/QalyCalc.R")
source("R/CostCalc.R")
set.seed(123)

```

# Load best fit parameters
```{r}
load("Best_theta_Param")
```

# OWA sensitivity analysis
```{r}

DistEdad<-vector(length=85)
DistEdad[1:10]<-0.114106384/10
DistEdad[11:20]<-0.116645332/10
DistEdad[21:30]<-0.281029342/10
DistEdad[31:40]<-0.30552628/10
DistEdad[41:50]<-0.112127906/10
DistEdad[51:85]<-0.070564755/35

Age<-85
years<-20

NoSem<-52
NumHSH<-892955-best_theta[1] #(INE)
NumHSHVIH<-best_theta[1]  #Encuesta hospitalaria

ACD4<-best_theta[2] #Distribucion de los pacientes por rango de CD4 (AIDS + CD4 <200, merged)
I7CD4<-best_theta[3] #200-350
Rest<-best_theta[4]   #>350
PropTR<-best_theta[5]

#Values 
G<-best_theta[6]  #Population growth rate 1/1000 anually
m<-read.csv("MortPobGen.csv", header=TRUE, sep=";")  #Mortality general population
mVIH235<-best_theta[7] #Mortality CD4 200-350; Alejos et al Medicine 2016
mVIH35<-best_theta[8]  #Mortality CD4 >350; Alejos et al Medicine 2016
mAIDS<-best_theta[9]   #Parastu et al PLOSone 2018
Cvh<-best_theta[10] #Partner change rate in the very high group 18-123/year Nichols et al. 2016
Ch<-best_theta[11]     #Partner change rate in the high group 5-18/year Nichols et al. 2016
Cl<-best_theta[12]   #Partner change rate in the low group 0.5-5/year Nichols et al. 2016
Cvl<-best_theta[13]  #Partner change rate in the very low group 0.04-0.5/year Nichols et al. 2016
nvh<-best_theta[14]     #Proportion of the total population in each group 5-15% Nichols et al. 2016
nh<-best_theta[15]     #30-50% Nichols et al. 2016
nl<-best_theta[16]     #10-35% Nichols et al. 2016
nvl<-best_theta[17]    #4-46%

B<-best_theta[18]  #per partnership transmissibility Nichols et al 2016.
I12<-best_theta[19] #1 month duration in stage 1 of HIV infection
I23<-best_theta[20] #1 month duration in stage 2 of HIV infection
I34<-best_theta[21] #1 month duration in stage 3 of HIV infection
I45<-best_theta[22] #3 month duration in stage 4 of HIV infection
I56<-best_theta[23] #3 month duration in stage 5 of HIV infection
I67<-best_theta[24] #Chronic duration in stage 6 of HIV infection
I78<-best_theta[25] #Chronic duration in stage 7 of HIV infection

PTr<-c(best_theta[26],best_theta[27],best_theta[28]) #Nuñez et al AIDS 2018

Woff <- 0.0038 #Proportion of people who go off PrEP. SiPrEP 15% anual, p=1-e^-rt
W<-0.00192    #Proportion of people who go on PrEP. SiPrEP describe 5000-7000 nuevos anuales y eso supone una probabilidad alrededor de 0.1 anual.RiskRed<-1-0.86 # 0.86 for TDF, 0.934 for TAF and 0.952 for CBV 0.96 for LCA
WAIDS<-0.7/52  
WHIV<-0.84/52
WM350<-0.94/52
WTREAT<-0.96/52    
WSusceptible<-1/52
Treatcost<-188.54
AIDScost<-19000/52
PrEPcost<-26.34 # TDF/FTC 26.34, 
```
```{r}
OWSAmat<-matrix(ncol=4, nrow=31, dimnames=list(NULL, c("QALYsl", "Costsl", "QALYsh", "Costsh")))
```

## 1. NumHSHVIH
### Low estimate
```{r}
NumHSHVIH<-best_theta[1]-best_theta[1]*0.2
NumHSH<-892955-NumHSHVIH

QP<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH,
                 ACD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mVIH235, mVIH35, mAIDS,
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B, 
                 I12, I23, I34, 
                 I45, I56, I67, 
                 I78, PTr, years, PropTR, RiskRed = 1-0.86)

l1<-QALYCostP(QP)
l1
OWSAmat[1,1:2]<-l1
OWSAmat
```

### High estimate
```{r}

NumHSHVIH<-best_theta[1]+best_theta[1]*0.2
NumHSH<-892955-NumHSHVIH

QP<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mVIH235, mVIH35, mAIDS,
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I56, I67, 
                 I78, PTr, years,PropTR, RiskRed = 1-0.86)

h1<-QALYCostP(QP)
OWSAmat[1,3:4]<-h1
OWSAmat

NumHSHVIH<-best_theta[1]
NumHSH<-892955-NumHSHVIH
```

## 2. % pacientes con CD4 menor de 200
### Low estimate
```{r}
ACD4<-best_theta[2]-best_theta[2]*0.2
QP<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mVIH235, mVIH35, mAIDS,
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I56, I67, 
                 I78, PTr, years, PropTR, RiskRed = 1-0.86)
l2<-QALYCostP(QP)
OWSAmat[2,1:2]<-l2
```

### High estimate
```{r}
ACD4<-best_theta[2]+best_theta[2]*0.2

QP<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4<-best_theta[2]+best_theta[2]*0.2, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mVIH235, mVIH35, mAIDS,
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I56, I67, 
                 I78, PTr, years, PropTR, RiskRed = 1-0.86)

h2<-QALYCostP(QP)
OWSAmat[2,3:4]<-h2
OWSAmat
ACD4<-best_theta[2]
```


## 4. % pacientes con CD4 entre 350-500
### Low estimate
```{r}
I7CD4<-best_theta[3]-best_theta[3]*0.2
Q<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mVIH235, mVIH35, mAIDS,
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I56, I67, 
                 I78, PTr, years, PropTR, RiskRed = 1-0.86)
l4<-QALYCostP(Q)
OWSAmat[3,1:2]<-l4
```

### High estimate
```{r}
I7CD4<-best_theta[3]+best_theta[3]*0.2
Q<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I7CD4=best_theta[3]+best_theta[3]*0.2, Rest, 
                 G, Woff, W, 
                 m, mVIH235, mVIH35, mAIDS,
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I56, I67, 
                 I78, PTr, years, PropTR, RiskRed = 1-0.86)

h4<-QALYCostP(Q)
OWSAmat[3,3:4]<-h4
OWSAmat
I7CD4=best_theta[3]
```

## 5. % pacientes con CD4 mayor de 500
### Low estimate
```{r}
Rest<-best_theta[4]-best_theta[4]*0.2
Q<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I7CD4, Rest=best_theta[4]-best_theta[4]*0.2, 
                 G, Woff, W, 
                 m, mVIH235, mVIH35, mAIDS,
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I56, I67, 
                 I78, PTr, years, PropTR, RiskRed = 1-0.86)
l5<-QALYCostP(Q)
OWSAmat[4,1:2]<-l5
```

### High estimate
```{r}
Rest<-best_theta[4]+best_theta[4]*0.2
Q<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I7CD4, Rest=best_theta[4]+best_theta[4]*0.2, 
                 G, Woff, W, 
                 m, mVIH235, mVIH35, mAIDS,
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I56, I67, 
                 I78, PTr, years, PropTR, RiskRed = 1-0.86)

h5<-QALYCostP(Q)
OWSAmat[4,3:4]<-h5
OWSAmat
Rest<-best_theta[4]
```
## 6. Proportion on treatment
### Low estimate
```{r}
PropTR<-max(0, best_theta[5]*0.8)
Q<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mVIH235, mVIH35, mAIDS,
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I56, I67, 
                 I78, PTr, years, PropTR=max(0, best_theta[5]*0.8), RiskRed = 1-0.86)
l6<-QALYCostP(Q)
OWSAmat[5,1:2]<-l6
```

### High estimate
```{r}
PropTR<-min(0.9999, best_theta[5]+best_theta[5]*0.2)

Q<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mVIH235, mVIH35, mAIDS,
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I56, I67, 
                 I78, PTr, years, PropTR=min(0.9999, best_theta[5]+best_theta[5]*0.2), RiskRed = 1-0.86)

h6<-QALYCostP(Q)
OWSAmat[5,3:4]<-h6
OWSAmat
PropTR<-best_theta[5]
```

## 7. Population growth
### Low estimate
```{r}
G<-best_theta[6]-best_theta[6]*0.2
Q<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mVIH235, mVIH35, mAIDS,
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I56, I67, 
                 I78, PTr, years, PropTR=PropTR, RiskRed = 1-0.86)
l7<-QALYCostP(Q)
OWSAmat[6,1:2]<-l7
```

### High estimate
```{r}
G<-best_theta[6]+best_theta[6]*0.2
Q<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mVIH235, mVIH35, mAIDS,
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I56, I67, 
                 I78, PTr, years,PropTR=PropTR, RiskRed = 1-0.86)
h7<-QALYCostP(Q)
OWSAmat[6,3:4]<-h7
G<-best_theta[6]
```

## 8. Mortality HIV 200-350 CD4
### Low estimate
```{r}
mVIH235=best_theta[7]-best_theta[7]*0.2
Q<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mVIH235, mVIH35, mAIDS,
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I56, I67, 
                 I78, PTr, years, PropTR=PropTR, RiskRed = 1-0.86)
l8<-QALYCostP(Q)
OWSAmat[7,1:2]<-l8
```

### High estimate
```{r}
mVIH235=best_theta[7]+best_theta[7]*0.2
Q<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mVIH235, mVIH35, mAIDS,
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I56, I67, 
                 I78, PTr, years, PropTR=PropTR, RiskRed = 1-0.86)
h8<-QALYCostP(Q)
OWSAmat[7,3:4]<-h8
OWSAmat
mVIH235<-best_theta[7]
```

## 9. Mortality HIV >350 CD4
### Low estimate
```{r}
mVIH35=best_theta[8]-best_theta[8]*0.2
Q<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mVIH235, mVIH35, mAIDS,
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I56, I67, 
                 I78, PTr, years, PropTR=PropTR, RiskRed = 1-0.86)
l9<-QALYCostP(Q)
OWSAmat[8,1:2]<-l9
```

### High estimate
```{r}
mVIH35=best_theta[8]+best_theta[8]*0.2
Q<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mVIH235, mVIH35, mAIDS,
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I56, I67, 
                 I78, PTr, years, PropTR=PropTR, RiskRed = 1-0.86)
h9<-QALYCostP(Q)
OWSAmat[8,3:4]<-h9
OWSAmat
mVIH35<-best_theta[8]
```

## 10. Mortality AIDS
### Low estimate
```{r}
mAIDS=(best_theta[9]-best_theta[9]*0.2)
Q<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mVIH235, mVIH35, mAIDS,
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I56, I67, 
                 I78, PTr, years, PropTR=PropTR, RiskRed = 1-0.86)

l10<-QALYCostP(Q)
OWSAmat[9,1:2]<-l10
```

### High estimate
```{r}
mAIDS=best_theta[9]+best_theta[9]*0.2
Q<-HIVSIMPREP(Age=85, NoSem=52, NumHSH, NumHSHVIH, 
                 ACD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mVIH235, mVIH35, mAIDS,
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I56, I67, 
                 I78, PTr, years=20, PropTR=PropTR, RiskRed = 1-0.86)
h10<-QALYCostP(Q)
OWSAmat[9,3:4]<-h10
mAIDS<-best_theta[9]
```

## 11. Cvh Partner change rate in very hig risk group
### Low estimate
```{r}
Cvh<-best_theta[10]-best_theta[10]*0.2
Q<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mVIH235, mVIH35, mAIDS,
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, I45, I56, I67, 
                 I78, PTr, years, PropTR=PropTR, RiskRed = 1-0.86)
l11<-QALYCostP(Q)
OWSAmat[10,1:2]<-l11
```

### High estimate
```{r}
Cvh<-best_theta[10]+best_theta[10]*0.2
Q<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mVIH235, mVIH35, mAIDS,
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I56, I67, 
                 I78, PTr, years, PropTR=PropTR, RiskRed = 1-0.86)
h11<-QALYCostP(Q)
OWSAmat[10,3:4]<-h11
OWSAmat
Cvh<-best_theta[10]
```

## 12. Ch Partner change rate in high risk group
### Low estimate
```{r}
Ch<-best_theta[11]-best_theta[11]*0.2
Q<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mVIH235, mVIH35, mAIDS,
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I56, I67, 
                 I78, PTr, years, PropTR=PropTR, RiskRed = 1-0.86)
l12<-QALYCostP(Q)
OWSAmat[11,1:2]<-l12
```

### High estimate
```{r}
Ch<-best_theta[11]+best_theta[11]*0.2
Q<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mVIH235, mVIH35, mAIDS,
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I56, I67, 
                 I78, PTr, years, PropTR=PropTR, RiskRed = 1-0.86)
h12<-QALYCostP(Q)
OWSAmat[11,3:4]<-h12
OWSAmat
Ch<-best_theta[11]
```

## 13. Cl Partner change rate in low risk group
### Low estimate
```{r}
Cl<-best_theta[12]-best_theta[12]*0.2
Q<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mVIH235, mVIH35, mAIDS,
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I56, I67, 
                 I78, PTr, years, PropTR=PropTR, RiskRed = 1-0.86)
l13<-QALYCostP(Q)
OWSAmat[12,1:2]<-l13
```

### High estimate
```{r}
Cl<-best_theta[12]+best_theta[12]*0.2
Q<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mVIH235, mVIH35, mAIDS,
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I56, I67, 
                 I78, PTr, years, PropTR=PropTR, RiskRed = 1-0.86)
h13<-QALYCostP(Q)
OWSAmat[12,3:4]<-h13
OWSAmat
Cl<-best_theta[12]
```

## 14. Cvl Partner change rate in very low risk group
### Low estimate
```{r}
Cvl<-best_theta[13]-best_theta[13]*0.2
Q<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mVIH235, mVIH35, mAIDS,
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I56, I67, 
                 I78, PTr, years, PropTR=PropTR, RiskRed = 1-0.86)
l14<-QALYCostP(Q)
OWSAmat[13,1:2]<-l14
```

### High estimate
```{r}
Cvl<-best_theta[13]+best_theta[13]*0.2
Q<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mVIH235, mVIH35, mAIDS,
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I56, I67, 
                 I78, PTr, years, PropTR=PropTR, RiskRed = 1-0.86)
h14<-QALYCostP(Q)
OWSAmat[13,3:4]<-h14
OWSAmat
Cvl<-best_theta[13]
```

## 15. nvh proportion of the population in each group
### Low estimate
```{r}
nvh<-best_theta[14]-best_theta[14]*0.2
Q<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mVIH235, mVIH35, mAIDS,
                 Cvh, Ch, Cl, Cvl, 
                 nvh=best_theta[14]-best_theta[14]*0.2, nh, nl, nvl, B,
                 I12, I23, I34,
                 I45, I56, I67, 
                 I78, PTr, years, PropTR=PropTR, RiskRed = 1-0.86)
l15<-QALYCostP(Q)
OWSAmat[14,1:2]<-l15
```

### High estimate
```{r}
nvh<-best_theta[14]+best_theta[14]*0.2
Q<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mVIH235, mVIH35, mAIDS,
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I56, I67, 
                 I78, PTr, years, PropTR=PropTR, RiskRed = 1-0.86)
h15<-QALYCostP(Q)
OWSAmat[14,3:4]<-h15
OWSAmat
nvh<-best_theta[14]
```

## 16. nh proportion of the population in each group
### Low estimate
```{r}
nh<-best_theta[15]-best_theta[15]*0.2
Q<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mVIH235, mVIH35, mAIDS,
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I56, I67, 
                 I78, PTr, years, PropTR=PropTR, RiskRed = 1-0.86)
l16<-QALYCostP(Q)
OWSAmat[15,1:2]<-l16
```

### High estimate
```{r}
nh=best_theta[15]+best_theta[15]*0.2
Q<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mVIH235, mVIH35, mAIDS,
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I56, I67, 
                 I78, PTr, years, PropTR=PropTR, RiskRed = 1-0.86)
h16<-QALYCostP(Q)
OWSAmat[15,3:4]<-h16
OWSAmat
nh<-best_theta[15]
```

## 17. nl proportion of the population in each group
### Low estimate
```{r}
nl<-best_theta[16]-best_theta[16]*0.2
Q<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mVIH235, mVIH35, mAIDS,
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I56, I67, 
                 I78, PTr, years, PropTR=PropTR, RiskRed = 1-0.86)
l17<-QALYCostP(Q)
OWSAmat[16,1:2]<-l17
```

### High estimate
```{r}
nl=best_theta[16]+best_theta[16]*0.2
Q<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mVIH235, mVIH35, mAIDS,
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl=best_theta[16]+best_theta[16]*0.2, nvl, B,
                 I12, I23, I34,
                 I45, I56, I67, 
                 I78, PTr, years, PropTR=PropTR, RiskRed = 1-0.86)
h17<-QALYCostP(Q)
OWSAmat[16,3:4]<-h17
OWSAmat
nl<-best_theta[16]
```

## 18. nvl proportion of the population in each group
### Low estimate
```{r}
nvl<-best_theta[17]-best_theta[17]*0.2
Q<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mVIH235, mVIH35, mAIDS,
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I56, I67, 
                 I78, PTr, years, PropTR=PropTR, RiskRed = 1-0.86)
l18<-QALYCostP(Q)
OWSAmat[17,1:2]<-l18
```

### High estimate
```{r}
nvl<-best_theta[17]+best_theta[17]*0.2
Q<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mVIH235, mVIH35, mAIDS,
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl=best_theta[17]+best_theta[17]*0.2, B,
                 I12, I23, I34, 
                 I45, I56, I67, 
                 I78, PTr, years, PropTR=PropTR, RiskRed = 1-0.86)
h18<-QALYCostP(Q)
OWSAmat[17,3:4]<-h18
OWSAmat
nvl<-best_theta[17]
```

## 19. B per partnership transmissibility 
### Low estimate
```{r}
B<-best_theta[18]-best_theta[18]*0.2
Q<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mVIH235, mVIH35, mAIDS,
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B=best_theta[18]-best_theta[18]*0.2,
                 I12, I23, I34, 
                 I45, I56, I67, 
                 I78, PTr, years, PropTR=PropTR, RiskRed = 1-0.86)
l19<-QALYCostP(Q)
OWSAmat[18,1:2]<-l19
```

### High estimate
```{r}
B<-best_theta[18]+best_theta[18]*0.2
Q<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mVIH235, mVIH35, mAIDS,
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B=best_theta[18]+best_theta[18]*0.2,
                 I12, I23, I34, 
                 I45, I56, I67, 
                 I78, PTr, years, PropTR=PropTR, RiskRed = 1-0.86)
h19<-QALYCostP(Q)
OWSAmat[18,3:4]<-h19
OWSAmat
B<-best_theta[18]
```

## 20. I12, 1 month duration in stage 1 of HIV infection
### Low estimate
```{r}
I12<-best_theta[19]-best_theta[19]*0.2
Q<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mVIH235, mVIH35, mAIDS,
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I56, I67, 
                 I78, PTr, years, PropTR=PropTR, RiskRed = 1-0.86)
l20<-QALYCostP(Q)
OWSAmat[19,1:2]<-l20
```

### High estimate
```{r}
I12<-best_theta[19]+best_theta[19]*0.2
Q<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mVIH235, mVIH35, mAIDS,
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I56, I67, 
                 I78, PTr, years, PropTR=PropTR, RiskRed = 1-0.86)
h20<-QALYCostP(Q)
OWSAmat[19,3:4]<-h20
OWSAmat
I12<-best_theta[19]
```

## 21. I23, 1 month duration in stage 2 of HIV infection
### Low estimate
```{r}
I23<-best_theta[20]-best_theta[20]*0.2
Q<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mVIH235, mVIH35, mAIDS,
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I56, I67, 
                 I78, PTr, years, PropTR=PropTR, RiskRed = 1-0.86)
l21<-QALYCostP(Q)
OWSAmat[20,1:2]<-l21
```

### High estimate
```{r}
I23<-best_theta[20]+best_theta[20]*0.2
Q<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mVIH235, mVIH35, mAIDS,
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I56, I67, 
                 I78, PTr, years, PropTR=PropTR, RiskRed = 1-0.86)
h21<-QALYCostP(Q)
OWSAmat[20,3:4]<-h21
OWSAmat
I23<-best_theta[20]
```

## 22. I34, 1 month duration in stage 3 of HIV infection
### Low estimate
```{r}
I34<-best_theta[21]-best_theta[21]*0.2
Q<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mVIH235, mVIH35, mAIDS,
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I56, I67, 
                 I78, PTr, years, PropTR=PropTR, RiskRed = 1-0.86)
l22<-QALYCostP(Q)
OWSAmat[21,1:2]<-l22
```

### High estimate
```{r}
I34<-best_theta[21]+best_theta[21]*0.2
Q<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mVIH235, mVIH35, mAIDS,
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I56, I67, 
                 I78, PTr, years, PropTR=PropTR, RiskRed = 1-0.86)
h22<-QALYCostP(Q)
OWSAmat[21,3:4]<-h22
OWSAmat
I34<-best_theta[21]
```

## 23. I45, 3 month duration in stage 4 of HIV infection
### Low estimate
```{r}
I45<-best_theta[22]-best_theta[22]*0.2
Q<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mVIH235, mVIH35, mAIDS,
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I56, I67, 
                 I78, PTr, years, PropTR=PropTR, RiskRed = 1-0.86)
l23<-QALYCostP(Q)
OWSAmat[22,1:2]<-l23
```

### High estimate
```{r}
I45=best_theta[22]+best_theta[22]*0.2
Q<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mVIH235, mVIH35, mAIDS,
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I56, I67, 
                 I78, PTr, years, PropTR=PropTR, RiskRed = 1-0.86)
h23<-QALYCostP(Q)
OWSAmat[22,3:4]<-h23
OWSAmat
I45<-best_theta[22]
```

## 26. I56, 3 month duration in stage 5 of HIV infection
### Low estimate
```{r}
I56<-best_theta[23]-best_theta[23]*0.2
Q<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mVIH235, mVIH35, mAIDS,
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I56, I67, 
                 I78, PTr, years, PropTR=PropTR, RiskRed = 1-0.86)
l26<-QALYCostP(Q)
OWSAmat[23,1:2]<-l26
```

### High estimate
```{r}
I56<-best_theta[23]+best_theta[23]*0.2
Q<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mVIH235, mVIH35, mAIDS,
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I56, I67, 
                 I78, PTr, years, PropTR=PropTR, RiskRed = 1-0.86)
h26<-QALYCostP(Q)
OWSAmat[23,3:4]<-h26
OWSAmat
I56<-best_theta[23]
```

## 27. I67, 3 month duration in stage 6 of HIV infection
### Low estimate
```{r}
I67<-best_theta[24]-best_theta[24]*0.2
Q<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mVIH235, mVIH35, mAIDS,
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I56, I67, 
                 I78, PTr, years, PropTR=PropTR, RiskRed = 1-0.86)
l27<-QALYCostP(Q)
OWSAmat[24,1:2]<-l27
```

### High estimate
```{r}
I67<-best_theta[24]+best_theta[24]*0.2
Q<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mVIH235, mVIH35, mAIDS,
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I56, I67, 
                 I78, PTr, years, PropTR=PropTR, RiskRed = 1-0.86)
h27<-QALYCostP(Q)
OWSAmat[24,3:4]<-h27
OWSAmat
I67<-best_theta[24]
```

## 28. I78, Chronic duration in stage 7
### Low estimate
```{r}
I78<-best_theta[25]-best_theta[25]*0.2
Q<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mVIH235, mVIH35, mAIDS,
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I56, I67, 
                 I78, PTr, years, PropTR=PropTR, RiskRed = 1-0.86)
l28<-QALYCostP(Q)
OWSAmat[25,1:2]<-l28
```

### High estimate
```{r}
I78<-best_theta[25]+best_theta[25]*0.2
Q<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mVIH235, mVIH35, mAIDS,
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I56, I67, 
                 I78, PTr, years, PropTR=PropTR, RiskRed = 1-0.86)
h28<-QALYCostP(Q)
OWSAmat[25,3:4]<-h28
OWSAmat
I78<-best_theta[25]
```


## 30. PTr[1], Probaility of starting treatment
### Low estimate
```{r}
PTr<-c(best_theta[26]-best_theta[26]*0.2,best_theta[27],best_theta[28])
Q<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mVIH235, mVIH35, mAIDS,
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I56, I67, 
                 I78, PTr, years, PropTR=PropTR, RiskRed = 1-0.86)
l30<-QALYCostP(Q)
OWSAmat[26,1:2]<-l30
```

### High estimate
```{r}
PTr<-c(best_theta[26]+best_theta[26]*0.2,best_theta[27],best_theta[28])
Q<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mVIH235, mVIH35, mAIDS,
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I56, I67, 
                 I78, PTr=c(best_theta[26]+best_theta[26]*0.2,best_theta[27],best_theta[28]), years, PropTR=PropTR, RiskRed = 1-0.86)
h30<-QALYCostP(Q)
OWSAmat[26,3:4]<-h30
OWSAmat
PTr<-c(best_theta[26],best_theta[27],best_theta[28])
```


## 31. PTr[2], Probaility of starting treatment
### Low estimate
```{r}
PTr<-c(best_theta[26],best_theta[27]-best_theta[27]*0.2,best_theta[28])
Q<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mVIH235, mVIH35, mAIDS,
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I56, I67, 
                 I78, PTr, years, PropTR=PropTR, RiskRed = 1-0.86)
l31<-QALYCostP(Q)
OWSAmat[27,1:2]<-l31
```

### High estimate
```{r}
PTr<-c(best_theta[26],best_theta[27]+best_theta[27]*0.2,best_theta[28])
Q<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mVIH235, mVIH35, mAIDS,
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I56, I67, 
                 I78, PTr, years, PropTR=PropTR, RiskRed = 1-0.86)
h31<-QALYCostP(Q)
OWSAmat[27,3:4]<-h31
OWSAmat
PTr<-c(best_theta[26],best_theta[27],best_theta[28])
```

## 32. PTr[3], Probaility of starting treatment
### Low estimate
```{r}
PTr<-c(best_theta[26],best_theta[27],best_theta[28]-best_theta[28]*0.2)
Q<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mVIH235, mVIH35, mAIDS,
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I56, I67, 
                 I78, PTr, years, PropTR=PropTR, RiskRed = 1-0.86)
l32<-QALYCostP(Q)
OWSAmat[28,1:2]<-l32
```

### High estimate
```{r}
PTr<-c(best_theta[26],best_theta[27],best_theta[28]+best_theta[28]*0.2)
Q<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mVIH235, mVIH35, mAIDS,
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I56, I67, 
                 I78, PTr, years, PropTR=PropTR, RiskRed = 1-0.86)
h32<-QALYCostP(Q)
OWSAmat[28,3:4]<-h32
OWSAmat
PTr<-c(best_theta[26],best_theta[27],best_theta[28])
```
## Impacto de la adherencia
### High estimate 
```{r}

Q<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mVIH235, mVIH35, mAIDS,
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I56, I67, 
                 I78, PTr, years, PropTR=PropTR, RiskRed = 1-0.86)
h33<-QALYCostP(Q)
OWSAmat[29,3:4]<-h33

OWSAmat
```
### Low estimate
```{r}

Q<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mVIH235, mVIH35, mAIDS,
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I56, I67, 
                 I78, PTr, years, PropTR=PropTR, RiskRed = (1-0.86)/0.7)
l33<-QALYCostP(Q)
OWSAmat[29,1:2]<-l33
OWSAmat
```

## 30. W (PrEP uptake rate)
### Low estimate
```{r}
W_base <- 0.00192
Q<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH,
                 ACD4, I7CD4, Rest,
                 G, Woff, W = W_base * 0.8,
                 m, mVIH235, mVIH35, mAIDS,
                 Cvh, Ch, Cl, Cvl,
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34,
                 I45, I56, I67,
                 I78, PTr, years, PropTR, RiskRed = 1-0.86)
l34<-QALYCostP(Q)
OWSAmat[30,1:2]<-l34
```
### High estimate
```{r}
Q<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH,
                 ACD4, I7CD4, Rest,
                 G, Woff, W = W_base * 1.2,
                 m, mVIH235, mVIH35, mAIDS,
                 Cvh, Ch, Cl, Cvl,
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34,
                 I45, I56, I67,
                 I78, PTr, years, PropTR, RiskRed = 1-0.86)
h34<-QALYCostP(Q)
OWSAmat[30,3:4]<-h34
OWSAmat
```

## 31. Woff (PrEP discontinuation rate)
### Low estimate
```{r}
Woff_base <- 0.0038
Q<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH,
                 ACD4, I7CD4, Rest,
                 G, Woff = Woff_base * 0.8, W,
                 m, mVIH235, mVIH35, mAIDS,
                 Cvh, Ch, Cl, Cvl,
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34,
                 I45, I56, I67,
                 I78, PTr, years, PropTR, RiskRed = 1-0.86)
l35<-QALYCostP(Q)
OWSAmat[31,1:2]<-l35
```
### High estimate
```{r}
Q<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH,
                 ACD4, I7CD4, Rest,
                 G, Woff = Woff_base * 1.2, W,
                 m, mVIH235, mVIH35, mAIDS,
                 Cvh, Ch, Cl, Cvl,
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34,
                 I45, I56, I67,
                 I78, PTr, years, PropTR, RiskRed = 1-0.86)
h35<-QALYCostP(Q)
OWSAmat[31,3:4]<-h35
OWSAmat
```

############################################################################################################-------Análisis OWA PrEP LCA----------############################################
#############################################################################################
```{r}
source("HIVSIM05.R")
source("QALYCostP.R")
Woff      <- 0.0038 #Proportion of people who go off PrEP. SiPrEP 15% anual, p=1-e^-rt
W<-0.00192    #Proportion of people who go on PrEP. SiPrEP describe 5000-7000 nuevos anuales y eso supone una probabilidad alrededor de 0.1 anual.
PrEPcost<-898.25 #LCA 898.25  
RiskRed<-1-0.96 
```
```{r}
OWSAmatP<-matrix(ncol=4, nrow=31, dimnames=list(NULL, c("QALYslP", "CostslP", "QALYshP", "CostshP")))
```




## 1. NumHSHVIH
### Low estimate
```{r}
NumHSHVIH<-best_theta[1]-best_theta[1]*0.2
NumHSH<-892955-NumHSHVIH 

QP<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mVIH235, mVIH35, mAIDS,
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B, RiskRed=1-0.96, 
                 I12, I23, I34, 
                 I45, I56, I67, 
                 I78, PTr, years)

l1P<-QALYCostP(QP)
l1P
OWSAmatP[1,1:2]<-l1P
OWSAmatP
```

### High estimate
```{r}
NumHSHVIH<-best_theta[1]+best_theta[1]*0.2
NumHSH<-892955-NumHSHVIH 
QP<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mVIH235, mVIH35, mAIDS,
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B, RiskRed=1-0.96,
                 I12, I23, I34, 
                 I45, I56, I67, 
                 I78, PTr, years)

h1P<-QALYCostP(QP)
h1P
OWSAmatP[1,3:4]<-h1P
OWSAmatP
NumHSHVIH<-best_theta[1]
NumHSH<-892955-NumHSHVIH 
```

## 2. % pacientes con CD4 menor de 200
### Low estimate
```{r}
ACD4<-best_theta[2]-best_theta[2]*0.2
QP<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mVIH235, mVIH35, mAIDS,
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B, RiskRed=1-0.96,
                 I12, I23, I34, 
                 I45, I56, I67, 
                 I78, PTr, years)
l2P<-QALYCostP(QP)
OWSAmatP[2,1:2]<-l2P
```

### High estimate
```{r}
ACD4<-best_theta[2]+best_theta[2]*0.2

QP<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mVIH235, mVIH35, mAIDS,
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B, RiskRed=1-0.96,
                 I12, I23, I34, 
                 I45, I56, I67, 
                 I78, PTr, years)

h2P<-QALYCostP(QP)
OWSAmatP[2,3:4]<-h2P
OWSAmatP
ACD4<-best_theta[2]
```


## 4. % pacientes con CD4 entre 350-500
### Low estimate
```{r}
I7CD4<-best_theta[3]-best_theta[3]*0.2
QP<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mVIH235, mVIH35, mAIDS,
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B, RiskRed=1-0.96,
                 I12, I23, I34, 
                 I45, I56, I67, 
                 I78, PTr, years)
l4P<-QALYCostP(QP)
OWSAmatP[3,1:2]<-l4P
```

### High estimate
```{r}
I7CD4=best_theta[3]+best_theta[3]*0.2
QP<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mVIH235, mVIH35, mAIDS,
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B, RiskRed=1-0.96,
                 I12, I23, I34, 
                 I45, I56, I67, 
                 I78, PTr, years)

h4P<-QALYCostP(QP)
OWSAmatP[3,3:4]<-h4P
OWSAmatP
I7CD4<-best_theta[3]
```

## 5. % pacientes con CD4 mayor de 500
### Low estimate
```{r}
Rest<-best_theta[4]-best_theta[4]*0.2
QP<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I7CD4, Rest=best_theta[4]-best_theta[4]*0.2, 
                 G, Woff, W, 
                 m, mVIH235, mVIH35, mAIDS,
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B, RiskRed=1-0.96,
                 I12, I23, I34, 
                 I45, I56, I67, 
                 I78, PTr, years)
l5P<-QALYCostP(QP)
OWSAmatP[4,1:2]<-l5P
```

### High estimate
```{r}
Rest<-best_theta[4]+best_theta[4]*0.2
QP<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I7CD4, Rest=best_theta[4]+best_theta[4]*0.2, 
                 G, Woff, W, 
                 m, mVIH235, mVIH35, mAIDS,
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B, RiskRed=1-0.96,
                 I12, I23, I34, 
                 I45, I56, I67, 
                 I78, PTr, years)

h5P<-QALYCostP(QP)
OWSAmatP[4,3:4]<-h5P
OWSAmatP
Rest<-best_theta[4]
```
## 6. Proportion on treatment
### Low estimate
```{r}
PropTR<-max(0, best_theta[5]*0.8)
QP<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mVIH235, mVIH35, mAIDS,
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B, RiskRed=1-0.96,
                 I12, I23, I34, 
                 I45, I56, I67, 
                 I78, PTr, years, PropTR=max(0, best_theta[5]*0.8))
l6P<-QALYCostP(QP)
OWSAmatP[5,1:2]<-l6P
```

### High estimate
```{r}
PropTR<-min(0.9999, best_theta[5]+best_theta[5]*0.2)
QP<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mVIH235, mVIH35, mAIDS,
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B, RiskRed=1-0.96,
                 I12, I23, I34, 
                 I45, I56, I67, 
                 I78, PTr, years, PropTR=min(0.9999, best_theta[5]+best_theta[5]*0.2))
               
h6P<-QALYCostP(QP)
OWSAmatP[5,3:4]<-h6P
OWSAmatP
PropTR<-best_theta[5]
```

## 7. Population growth
### Low estimate
```{r}
G<-best_theta[6]-best_theta[6]*0.2
QP<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mVIH235, mVIH35, mAIDS,
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B, RiskRed=1-0.96,
                 I12, I23, I34, 
                 I45, I56, I67, 
                 I78, PTr, years,PropTR)
l7P<-QALYCostP(QP)
OWSAmatP[6,1:2]<-l7P
```

### High estimate
```{r}
G<-best_theta[6]+best_theta[6]*0.2
QP<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mVIH235, mVIH35, mAIDS,
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B, RiskRed=1-0.96,
                 I12, I23, I34, 
                 I45, I56, I67, 
                 I78, PTr, years,PropTR)
h7P<-QALYCostP(QP)
OWSAmatP[6,3:4]<-h7P
OWSAmatP
G<-best_theta[6]
```

## 8. Mortality HIV 200-350 CD4
### Low estimate
```{r}
mVIH235<-best_theta[7]-best_theta[7]*0.2
QP<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mVIH235, mVIH35, mAIDS,
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B, RiskRed=1-0.96,
                 I12, I23, I34, 
                 I45, I56, I67, 
                 I78, PTr, years,PropTR)
l8P<-QALYCostP(QP)
OWSAmatP[7,1:2]<-l8P
```

### High estimate
```{r}
mVIH235<-best_theta[7]+best_theta[7]*0.2
QP<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mVIH235, mVIH35, mAIDS,
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B, RiskRed=1-0.96,
                 I12, I23, I34, 
                 I45, I56, I67, 
                 I78, PTr, years,PropTR)
h8P<-QALYCostP(QP)
OWSAmatP[7,3:4]<-h8P
OWSAmatP
mVIH235<-best_theta[7]
```

## 9. Mortality HIV >350 CD4
### Low estimate
```{r}
mVIH35<-best_theta[8]-best_theta[8]*0.2
QP<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mVIH235, mVIH35, mAIDS,
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B, RiskRed=1-0.96,
                 I12, I23, I34, 
                 I45, I56, I67, 
                 I78, PTr, years,PropTR)
l9P<-QALYCostP(QP)
OWSAmatP[8,1:2]<-l9P
```

### High estimate
```{r}
mVIH35<-best_theta[8]+best_theta[8]*0.2
QP<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mVIH235, mVIH35, mAIDS,
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B, RiskRed=1-0.96,
                 I12, I23, I34, 
                 I45, I56, I67, 
                 I78, PTr, years,PropTR)
h9P<-QALYCostP(QP)
OWSAmatP[8,3:4]<-h9P
OWSAmatP
mVIH35<-best_theta[8]
```

## 10. Mortality AIDS
### Low estimate
```{r}
mAIDS<-best_theta[9]-best_theta[9]*0.2
QP<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mVIH235, mVIH35, mAIDS,
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B, RiskRed=1-0.96,
                 I12, I23, I34, 
                 I45, I56, I67, 
                 I78, PTr, years,PropTR)
l10P<-QALYCostP(QP)
OWSAmatP[9,1:2]<-l10P
```

### High estimate
```{r}
mAIDS<-best_theta[9]+best_theta[9]*0.2
QP<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mVIH235, mVIH35, mAIDS,
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B, RiskRed=1-0.96,
                 I12, I23, I34, 
                 I45, I56, I67, 
                 I78, PTr, years,PropTR)
h10P<-QALYCostP(QP)
OWSAmatP[9,3:4]<-h10P
OWSAmatP
mAIDS<-best_theta[9]
```

## 11. Cvh Partner change rate in very hig risk group
### Low estimate
```{r}
Cvh<-best_theta[10]-best_theta[10]*0.2
QP<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mVIH235, mVIH35, mAIDS,
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B, RiskRed=1-0.96,
                 I12, I23, I34, 
                 I45, I56, I67, 
                 I78, PTr, years,PropTR)
l11P<-QALYCostP(QP)
OWSAmatP[10,1:2]<-l11P
```

### High estimate
```{r}
Cvh<-best_theta[10]+best_theta[10]*0.2
QP<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mVIH235, mVIH35, mAIDS,
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I56, I67, 
                 I78, PTr, years,PropTR)
h11P<-QALYCostP(QP)
OWSAmatP[10,3:4]<-h11P
OWSAmatP
Cvh<-best_theta[10]
```

## 12. Ch Partner change rate in high risk group
### Low estimate
```{r}
Ch<-best_theta[11]-best_theta[11]*0.2
QP<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mVIH235, mVIH35, mAIDS,
                 Cvh, Ch=best_theta[11]-best_theta[11]*0.2, Cl, Cvl, 
                 nvh, nh, nl, nvl, B, RiskRed=1-0.96,
                 I12, I23, I34, 
                 I45, I56, I67, 
                 I78, PTr, years,PropTR)
l12P<-QALYCostP(QP)
OWSAmatP[11,1:2]<-l12P
```

### High estimate
```{r}
Ch<-best_theta[11]+best_theta[11]*0.2
QP<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mVIH235, mVIH35, mAIDS,
                 Cvh, Ch=best_theta[11]+best_theta[11]*0.2, Cl, Cvl, 
                 nvh, nh, nl, nvl, B, RiskRed=1-0.96,
                 I12, I23, I34, 
                 I45, I56, I67, 
                 I78, PTr, years,PropTR)
h12P<-QALYCostP(QP)
OWSAmatP[11,3:4]<-h12P
OWSAmatP
Ch<-best_theta[11]
```

## 13. Cl Partner change rate in low risk group
### Low estimate
```{r}
Cl<-best_theta[12]-best_theta[12]*0.2
QP<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mVIH235, mVIH35, mAIDS,
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B, RiskRed=1-0.96,
                 I12, I23, I34, 
                 I45, I56, I67, 
                 I78, PTr, years,PropTR)
l13P<-QALYCostP(QP)
OWSAmatP[12,1:2]<-l13P
```

### High estimate
```{r}
Cl<-best_theta[12]+best_theta[12]*0.2
QP<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mVIH235, mVIH35, mAIDS,
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B, RiskRed=1-0.96,
                 I12, I23, I34, 
                 I45, I56, I67, 
                 I78, PTr, years,PropTR)
h13P<-QALYCostP(QP)
OWSAmatP[12,3:4]<-h13P
OWSAmatP
Cl<-best_theta[12]
```

## 14. Cvl Partner change rate in very low risk group
### Low estimate
```{r}
Cvl<-best_theta[13]-best_theta[13]*0.2
QP<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mVIH235, mVIH35, mAIDS,
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B, RiskRed=1-0.96,
                 I12, I23, I34, 
                 I45, I56, I67, 
                 I78, PTr, years, PropTR)
l14P<-QALYCostP(QP)
OWSAmatP[13,1:2]<-l14P
```

### High estimate
```{r}
Cvl<-best_theta[13]+best_theta[13]*0.2
QP<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mVIH235, mVIH35, mAIDS,
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B, RiskRed=1-0.96,
                 I12, I23, I34, 
                 I45, I56, I67, 
                 I78, PTr, years, PropTR)
h14P<-QALYCostP(QP)
OWSAmatP[13,3:4]<-h14P
OWSAmatP
Cvl<-best_theta[13]
```

## 15. nvh proportion of the population in each group
### Low estimate
```{r}
nvh<-best_theta[14]-best_theta[14]*0.2
QP<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mVIH235, mVIH35, mAIDS,
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B, RiskRed=1-0.96,
                 I12, I23, I34, 
                 I45, I56, I67, 
                 I78, PTr, years, PropTR)
l15P<-QALYCostP(QP)
OWSAmatP[14,1:2]<-l15P
```

### High estimate
```{r}
nvh<-best_theta[14]+best_theta[14]*0.2
QP<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mVIH235, mVIH35, mAIDS,
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B, RiskRed=1-0.96,
                 I12, I23, I34, 
                 I45, I56, I67, 
                 I78, PTr, years, PropTR)
h15P<-QALYCostP(QP)
OWSAmatP[14,3:4]<-h15P
OWSAmatP
nvh<-best_theta[14]
```

## 16. nh proportion of the population in each group
### Low estimate
```{r}
nh<-best_theta[15]-best_theta[15]*0.2
QP<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mVIH235, mVIH35, mAIDS,
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B, RiskRed=1-0.96,
                 I12, I23, I34, 
                 I45, I56, I67, 
                 I78, PTr, years, PropTR)
l16P<-QALYCostP(QP)
OWSAmatP[15,1:2]<-l16P
```

### High estimate
```{r}
nh<-best_theta[15]+best_theta[15]*0.2
QP<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mVIH235, mVIH35, mAIDS,
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B, RiskRed=1-0.96,
                 I12, I23, I34, 
                 I45, I56, I67, 
                 I78, PTr, years, PropTR)
h16P<-QALYCostP(QP)
OWSAmatP[15,3:4]<-h16P
OWSAmatP
nh<-best_theta[15]
```

## 17. nl proportion of the population in each group
### Low estimate
```{r}
nl<-best_theta[16]-best_theta[16]*0.2
QP<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mVIH235, mVIH35, mAIDS,
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B, RiskRed=1-0.96,
                 I12, I23, I34, 
                 I45, I56, I67, 
                 I78, PTr, years, PropTR)
l17P<-QALYCostP(QP)
OWSAmatP[16, 1:2]<-l17P
```

### High estimate
```{r}
nl<-best_theta[16]+best_theta[16]*0.2
QP<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mVIH235, mVIH35, mAIDS,
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B, RiskRed=1-0.96,
                 I12, I23, I34, 
                 I45, I56, I67, 
                 I78, PTr, years, PropTR)
h17P<-QALYCostP(QP)
OWSAmatP[16,3:4]<-h17P
OWSAmatP
nl<-best_theta[16]
```

## 18. nvl proportion of the population in each group
### Low estimate
```{r}
nvl<-best_theta[17]-best_theta[17]*0.2
QP<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mVIH235, mVIH35, mAIDS,
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B, RiskRed=1-0.96,
                 I12, I23, I34, 
                 I45, I56, I67, 
                 I78, PTr, years, PropTR)
l18P<-QALYCostP(QP)
OWSAmatP[17, 1:2]<-l18P
```

### High estimate
```{r}
nvl<-best_theta[17]+best_theta[17]*0.2
QP<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mVIH235, mVIH35, mAIDS,
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B, RiskRed=1-0.96,
                 I12, I23, I34, 
                 I45, I56, I67, 
                 I78, PTr, years, PropTR)
h18P<-QALYCostP(QP)
OWSAmatP[17,3:4]<-h18P
OWSAmatP
nvl<-best_theta[17]
```

## 19. B per partnership transmissibility 
### Low estimate
```{r}
B<-best_theta[18]-best_theta[18]*0.2
QP<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mVIH235, mVIH35, mAIDS,
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B, RiskRed=1-0.96,
                 I12, I23, I34, 
                 I45, I56, I67, 
                 I78, PTr, years, PropTR)
l19P<-QALYCostP(QP)
OWSAmatP[18, 1:2]<-l19P
```

### High estimate
```{r}
B<-best_theta[18]+best_theta[18]*0.2
QP<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mVIH235, mVIH35, mAIDS,
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B, RiskRed=1-0.96,
                 I12, I23, I34, 
                 I45, I56, I67, 
                 I78, PTr, years, PropTR)
h19P<-QALYCostP(QP)
OWSAmatP[18,3:4]<-h19P
OWSAmatP
B<-best_theta[18]
```

## 20. I12, 1 month duration in stage 1 of HIV infection
### Low estimate
```{r}
I12<-best_theta[19]-best_theta[19]*0.2
QP<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mVIH235, mVIH35, mAIDS,
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B, RiskRed=1-0.96,
                 I12, I23, I34, 
                 I45, I56, I67, 
                 I78, PTr, years, PropTR)
l20P<-QALYCostP(QP)
OWSAmatP[19, 1:2]<-l20P
```

### High estimate
```{r}
I12<-best_theta[19]+best_theta[19]*0.2
QP<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mVIH235, mVIH35, mAIDS,
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B, RiskRed=1-0.96,
                 I12, I23, I34, 
                 I45, I56, I67, 
                 I78, PTr, years, PropTR)
h20P<-QALYCostP(QP)
OWSAmatP[19,3:4]<-h20P
OWSAmatP
I12<-best_theta[19]
```

## 21. I23, 1 month duration in stage 2 of HIV infection
### Low estimate
```{r}
I23<-best_theta[20]-best_theta[20]*0.2
QP<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mVIH235, mVIH35, mAIDS,
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B, RiskRed=1-0.96,
                 I12, I23, I34, 
                 I45, I56, I67, 
                 I78, PTr, years, PropTR)
l21P<-QALYCostP(QP)
OWSAmatP[20, 1:2]<-l21P
```

### High estimate
```{r}
I23<-best_theta[20]+best_theta[20]*0.2
QP<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mVIH235, mVIH35, mAIDS,
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B, RiskRed=1-0.96,
                 I12, I23=best_theta[20]+best_theta[20]*0.2, I34, 
                 I45, I56, I67, 
                 I78, PTr, years, PropTR)
h21P<-QALYCostP(QP)
OWSAmatP[20,3:4]<-h21P
OWSAmatP
I23<-best_theta[20]
```

## 22. I34, 1 month duration in stage 3 of HIV infection
### Low estimate
```{r}
I34<-best_theta[21]-best_theta[21]*0.2
QP<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mVIH235, mVIH35, mAIDS,
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B, RiskRed=1-0.96,
                 I12, I23, I34=best_theta[21]-best_theta[21]*0.2, 
                 I45, I56, I67, 
                 I78, PTr, years, PropTR)
l22P<-QALYCostP(QP)
OWSAmatP[21, 1:2]<-l22P
```

### High estimate
```{r}
I34<-best_theta[21]+best_theta[21]*0.2
QP<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mVIH235, mVIH35, mAIDS,
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B, RiskRed=1-0.96,
                 I12, I23, I34, 
                 I45, I56, I67, 
                 I78, PTr, years, PropTR)
h22P<-QALYCostP(QP)
OWSAmatP[21,3:4]<-h22P
OWSAmatP
I34<-best_theta[21]
```

## 23. I45, 3 month duration in stage 4 of HIV infection
### Low estimate
```{r}
I45<-best_theta[22]-best_theta[22]*0.2
QP<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mVIH235, mVIH35, mAIDS,
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B, RiskRed=1-0.96,
                 I12, I23, I34, 
                 I45, I56, I67, 
                 I78, PTr, years, PropTR)
l23P<-QALYCostP(QP)
OWSAmatP[22, 1:2]<-l23P
```

### High estimate
```{r}
I45<-best_theta[22]+best_theta[22]*0.2
QP<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mVIH235, mVIH35, mAIDS,
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B, RiskRed=1-0.96,
                 I12, I23, I34, 
                 I45, I56, I67, 
                 I78, PTr, years, PropTR)
h23P<-QALYCostP(QP)
OWSAmatP[22,3:4]<-h23P
OWSAmatP
I45<-best_theta[22]
```

## 26. I56, 3 month duration in stage 5 of HIV infection
### Low estimate
```{r}
I56<-best_theta[23]-best_theta[23]*0.2
QP<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mVIH235, mVIH35, mAIDS,
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B, RiskRed=1-0.96,
                 I12, I23, I34, 
                 I45, I56, I67, 
                 I78, PTr, years, PropTR)
l26P<-QALYCostP(QP)
OWSAmatP[23, 1:2]<-l26P
```

### High estimate
```{r}
I56<-best_theta[23]+best_theta[23]*0.2
QP<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mVIH235, mVIH35, mAIDS,
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B, RiskRed=1-0.96,
                 I12, I23, I34, 
                 I45, I56, I67, 
                 I78, PTr, years, PropTR)
h26P<-QALYCostP(QP)
OWSAmatP[23,3:4]<-h26P
OWSAmatP
I56<-best_theta[23]
```

## 27. I67, 3 month duration in stage 6 of HIV infection
### Low estimate
```{r}
I67<-best_theta[24]-best_theta[24]*0.2
QP<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mVIH235, mVIH35, mAIDS,
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B, RiskRed=1-0.96,
                 I12, I23, I34, 
                 I45, I56, I67, 
                 I78, PTr, years, PropTR)
l27P<-QALYCostP(QP)
OWSAmatP[24, 1:2]<-l27P
```

### High estimate
```{r}
I67<-best_theta[24]+best_theta[24]*0.2
QP<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mVIH235, mVIH35, mAIDS,
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B, RiskRed=1-0.96,
                 I12, I23, I34, 
                 I45, I56, I67=best_theta[23]+best_theta[23]*0.2, 
                 I78, PTr, years, PropTR)
h27P<-QALYCostP(QP)
OWSAmatP[24,3:4]<-h27P
OWSAmatP
I67<-best_theta[24]
```

## 28. I78, Chronic duration in stage 7
### Low estimate
```{r}
I78=best_theta[25]-best_theta[25]*0.2
QP<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mVIH235, mVIH35, mAIDS,
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B, RiskRed=1-0.96,
                 I12, I23, I34, 
                 I45, I56, I67, 
                 I78, PTr, years, PropTR)
  l28P<-QALYCostP(QP)
OWSAmatP[25, 1:2]<-l28P
```

### High estimate
```{r}
I78<-best_theta[25]+best_theta[25]*0.2
QP<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mVIH235, mVIH35, mAIDS,
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B, RiskRed=1-0.96,
                 I12, I23, I34, 
                 I45, I56, I67, 
                 I78, PTr, years, PropTR)
h28P<-QALYCostP(QP)
OWSAmatP[25,3:4]<-h28P
OWSAmatP
I78<-best_theta[25]
```


## 30. PTr[1], Probaility of starting treatment
### Low estimate
```{r}
PTr<-c(best_theta[26]-best_theta[26]*0.2,best_theta[27],best_theta[28])
QP<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mVIH235, mVIH35, mAIDS,
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B, RiskRed=1-0.96,
                 I12, I23, I34, 
                 I45, I56, I67, 
                 I78, PTr, years, PropTR)
l30P<-QALYCostP(QP)
OWSAmatP[26, 1:2]<-l30P
```

### High estimate
```{r}
PTr<-c(best_theta[26]+best_theta[26]*0.2,best_theta[27],best_theta[28])
QP<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mVIH235, mVIH35, mAIDS,
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B, RiskRed=1-0.96,
                 I12, I23, I34, 
                 I45, I56, I67, 
                 I78, PTr, years, PropTR)
h30P<-QALYCostP(QP)
OWSAmatP[26,3:4]<-h30P
OWSAmatP
PTr<-c(best_theta[26],best_theta[27],best_theta[28])
```

## 31. PTr[2], Probaility of starting treatment
### Low estimate
```{r}
PTr<-c(best_theta[26],best_theta[27]-best_theta[27]*0.2,best_theta[28])
QP<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mVIH235, mVIH35, mAIDS,
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,RiskRed=1-0.96,
                 I12, I23, I34, 
                 I45, I56, I67, 
                 I78, PTr, years, PropTR)
l31P<-QALYCostP(QP)
OWSAmatP[27, 1:2]<-l31P
```

### High estimate
```{r}
PTr<-c(best_theta[26],best_theta[27]+best_theta[27]*0.2,best_theta[28])
QP<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mVIH235, mVIH35, mAIDS,
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,RiskRed=1-0.96,
                 I12, I23, I34, 
                 I45, I56, I67, 
                 I78, PTr, years, PropTR)
h31P<-QALYCostP(QP)
OWSAmatP[27,3:4]<-h31P
OWSAmatP
PTr<-c(best_theta[26],best_theta[27],best_theta[28])
```

## 32. PTr[3], Probaility of starting treatment
### Low estimate
```{r}
PTr<-c(best_theta[26],best_theta[27],best_theta[28]-best_theta[28]*0.2)
QP<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mVIH235, mVIH35, mAIDS,
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,RiskRed=1-0.96,
                 I12, I23, I34, 
                 I45, I56, I67, 
                 I78, PTr, years, PropTR)
l32P<-QALYCostP(QP)
OWSAmatP[28, 1:2]<-l32P
```

### High estimate
```{r}
PTr<-c(best_theta[26],best_theta[27],best_theta[28]+best_theta[28]*0.2)
QP<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mVIH235, mVIH35, mAIDS,
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,RiskRed=1-0.96,
                 I12, I23, I34, 
                 I45, I56, I67, 
                 I78, PTr, years, PropTR)
h32P<-QALYCostP(QP)
OWSAmatP[28,3:4]<-h32P
OWSAmatP
PTr<-c(best_theta[26],best_theta[27],best_theta[28])
```
## Impacto de la adherencia
### High estimate
```{r}
QP<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mVIH235, mVIH35, mAIDS,
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,RiskRed=1-0.96,
                 I12, I23, I34, 
                 I45, I56, I67, 
                 I78, PTr, years, PropTR)
h33<-QALYCostP(QP)
OWSAmatP[29,3:4]<-h33
OWSAmatP
```
### Low estimate
```{r}
QP<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mVIH235, mVIH35, mAIDS,
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,RiskRed=(1-0.96)/0.99,
                 I12, I23, I34, 
                 I45, I56, I67, 
                 I78, PTr, years, PropTR)
l33<-QALYCostP(QP)
OWSAmatP[29,1:2]<-l33
OWSAmatP
```

## 30. W (PrEP uptake rate)
### Low estimate
```{r}
W_base <- 0.00192
QP<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH,
                 ACD4, I7CD4, Rest,
                 G, Woff, W = W_base * 0.8,
                 m, mVIH235, mVIH35, mAIDS,
                 Cvh, Ch, Cl, Cvl,
                 nvh, nh, nl, nvl, B, RiskRed = 1-0.96,
                 I12, I23, I34,
                 I45, I56, I67,
                 I78, PTr, years, PropTR)
l34P<-QALYCostP(QP)
OWSAmatP[30,1:2]<-l34P
```
### High estimate
```{r}
QP<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH,
                 ACD4, I7CD4, Rest,
                 G, Woff, W = W_base * 1.2,
                 m, mVIH235, mVIH35, mAIDS,
                 Cvh, Ch, Cl, Cvl,
                 nvh, nh, nl, nvl, B, RiskRed = 1-0.96,
                 I12, I23, I34,
                 I45, I56, I67,
                 I78, PTr, years, PropTR)
h34P<-QALYCostP(QP)
OWSAmatP[30,3:4]<-h34P
OWSAmatP
```

## 31. Woff (PrEP discontinuation rate)
### Low estimate
```{r}
Woff_base <- 0.0038
QP<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH,
                 ACD4, I7CD4, Rest,
                 G, Woff = Woff_base * 0.8, W,
                 m, mVIH235, mVIH35, mAIDS,
                 Cvh, Ch, Cl, Cvl,
                 nvh, nh, nl, nvl, B, RiskRed = 1-0.96,
                 I12, I23, I34,
                 I45, I56, I67,
                 I78, PTr, years, PropTR)
l35P<-QALYCostP(QP)
OWSAmatP[31,1:2]<-l35P
```
### High estimate
```{r}
QP<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH,
                 ACD4, I7CD4, Rest,
                 G, Woff = Woff_base * 1.2, W,
                 m, mVIH235, mVIH35, mAIDS,
                 Cvh, Ch, Cl, Cvl,
                 nvh, nh, nl, nvl, B, RiskRed = 1-0.96,
                 I12, I23, I34,
                 I45, I56, I67,
                 I78, PTr, years, PropTR)
h35P<-QALYCostP(QP)
OWSAmatP[31,3:4]<-h35P
OWSAmatP
```

# Combine, save and export
```{r}
save(OWSAmat, file="OWSAmat_TDF")
save(OWSAmatP, file="OWSAmat_LCA")
load("OWSAmat_TDF")
load("OWSAmat_LCA")

OWSADAT<-cbind(OWSAmat, OWSAmatP)
save(OWSADAT, file="OWSADAT_TDF_LCA")
head(OWSADAT)
```

```{r}
ICER_Low<-(OWSADAT[,6]-OWSADAT[,2])/(OWSADAT[,5]-OWSADAT[,1])
ICER_High<-(OWSADAT[,8]-OWSADAT[,4])/(OWSADAT[,7]-OWSADAT[,3])
ICER_High
ICER_Low
Variable<-c("HIV-MSM", "ACD4", "I7CD4", "Rest","PropTR", "G","mVIH235","mVIH35","mAIDS","Cvh","Ch","Cl","Cvl","nvh","nh","nl","nvl","B","I12","I23","I34","I45","I56","I67","I78","PTr1", "PTr2", "PTr3", "Adherence", "W", "Woff")
ICER<-4783564
ICERS<-NULL
ICERS<-data.frame(Variable, ICER_High, ICER_Low, ICER)
ICERS$dif<-abs(ICERS$ICER_High-ICERS$ICER_Low)


ICERS$Direction <- ifelse(ICERS$ICER_High > ICERS$ICER_Low,
                          "Increase ICER",
                          "Decrease ICER")

# Cap extreme ICERs so the tornado plot is readable
axis_cap <- max(
  ICERS$ICER_High[is.finite(ICERS$ICER_High) & ICERS$ICER_High < quantile(ICERS$ICER_High[is.finite(ICERS$ICER_High)], 0.95) * 2],
  ICERS$ICER_Low[is.finite(ICERS$ICER_Low)],
  na.rm = TRUE
) * 1.15

# Descriptive but short labels for the tornado plot
ICERS$Variable <- recode(ICERS$Variable,
  "HIV-MSM"   = "GBMSM living with HIV",
  "ACD4"      = "Prop. CD4 < 200",
  "I7CD4"     = "Prop. CD4 200\u2013350",
  "Rest"      = "Prop. CD4 > 350",
  "PropTR"    = "Prop. on ART",
  "G"         = "Population growth",
  "mVIH235"   = "Mortality (CD4 200\u2013350)",
  "mVIH35"    = "Mortality (CD4 > 350)",
  "mAIDS"     = "AIDS mortality",
  "Cvh"       = "Partners (very high risk)",
  "Ch"        = "Partners (high risk)",
  "Cl"        = "Partners (low risk)",
  "Cvl"       = "Partners (very low risk)",
  "nvh"       = "Prop. very high risk",
  "nh"        = "Prop. high risk",
  "nl"        = "Prop. low risk",
  "nvl"       = "Prop. very low risk",
  "B"         = "Transmission prob.",
  "I12"       = "Progression I1\u2192I2",
  "I23"       = "Progression I2\u2192I3",
  "I34"       = "Progression I3\u2192I4",
  "I45"       = "Progression I4\u2192I5",
  "I56"       = "Progression I5\u2192I6",
  "I67"       = "Progression I6\u2192I7",
  "I78"       = "Progression I7\u2192I8",
  "PTr1"      = "ART rate (AIDS)",
  "PTr2"      = "ART rate (CD4 200\u2013350)",
  "PTr3"      = "ART rate (CD4 > 350)",
  "Adherence" = "PrEP adherence",
  "W"         = "PrEP uptake rate",
  "Woff"      = "PrEP discontinuation rate"
)

ICERS_plot <- ICERS
ICERS_plot$capped_high <- !is.finite(ICERS_plot$ICER_High) | ICERS_plot$ICER_High > axis_cap
ICERS_plot$capped_low  <- !is.finite(ICERS_plot$ICER_Low)  | ICERS_plot$ICER_Low  > axis_cap
ICERS_plot$ICER_High[ICERS_plot$capped_high] <- axis_cap
ICERS_plot$ICER_Low[ICERS_plot$capped_low]   <- axis_cap

# Reorder Variable by range, then identify capped bars
ICERS_plot$Variable <- fct_reorder(ICERS_plot$Variable, ICERS_plot$dif)
capped_rows <- ICERS_plot[ICERS_plot$capped_high | ICERS_plot$capped_low, ]

OWSATDFLCA <- ggplot(ICERS_plot, aes(x = Variable, y = ICER,
             ymin = ICER_Low, ymax = ICER_High,
             colour = Direction)) +
  geom_linerange(size = 3) +
  coord_flip() +
  geom_hline(yintercept = 4293887, col = "blue") +
  geom_hline(yintercept = 33895.59, col = "red") +
  annotate("segment",
           x = capped_rows$Variable, xend = capped_rows$Variable,
           y = axis_cap * 0.92, yend = axis_cap,
           arrow = arrow(length = unit(0.15, "cm"), type = "closed"),
           colour = "grey30") +
  scale_colour_manual(values = c("Increase ICER" = "#D55E00",
                                 "Decrease ICER" = "#0072B2")) +
  ylab("ICER") +
  theme_classic() +
  theme(plot.margin = unit(c(1,1,1,1), "cm"))

tiff("OWSATDF_LCA_01_R.tif", width=16, height=12, units="cm", res=300)
OWSATDFLCA
save(OWSATDFLCA, file="OWSATDF_LCA")
dev.off

```

## OWSA results table (Word export)
```{r owsa-word-table}
library(flextable)
library(officer)

# Base values for all 31 parameters
base_vals <- c(
  best_theta,                        # 1-28: calibrated parameters
  1 - 0.96,                          # 29: Adherence (RiskRed for LCA)
  0.00192,                           # 30: W (PrEP uptake rate)
  0.0038                             # 31: Woff (PrEP discontinuation rate)
)

owsa_tbl <- data.frame(
  Parameter  = as.character(ICERS$Variable),
  Base_Value = base_vals,
  Low_Value  = base_vals * 0.8,
  High_Value = base_vals * 1.2,
  ICER_Low   = ICERS$ICER_Low,
  ICER_High  = ICERS$ICER_High
)

# Adherence low was computed as RiskRed / 0.99, not *0.8
owsa_tbl$Low_Value[owsa_tbl$Parameter == "PrEP adherence"]  <- (1 - 0.96) / 0.99
owsa_tbl$High_Value[owsa_tbl$Parameter == "PrEP adherence"] <- 1 - 0.96

ft_owsa <- flextable(owsa_tbl) |>
  set_header_labels(
    Parameter  = "Parameter",
    Base_Value = "Base Value",
    Low_Value  = "Low Value",
    High_Value = "High Value",
    ICER_Low   = "ICER (Low)",
    ICER_High  = "ICER (High)"
  ) |>
  colformat_double(j = c("Base_Value", "Low_Value", "High_Value"), digits = 6) |>
  colformat_double(j = c("ICER_Low", "ICER_High"), digits = 0, big.mark = ",") |>
  autofit() |>
  theme_vanilla()

# Export to Word
doc <- read_docx() |>
  body_add_par("Table: One-Way Sensitivity Analysis Results", style = "heading 1") |>
  body_add_flextable(ft_owsa)

print(doc, target = "OWSA_Table.docx")
ft_owsa
```
