---
title: "Coste-eficacia de PrEP en España"
author: "Philip Wikman"
date: "sys.date()"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
source("QalyCalc.R")
source("CostCalc.R")
source("QALYCost.R")
set.seed(123)
```


# Dinamic HIV transmission model in HSH in Spain
##Values
```{r}
load("Best_theta_Param")
DistEdad<-vector(length=85)
DistEdad[1:10]<-0.114106384/10
DistEdad[11:20]<-0.116645332/10
DistEdad[21:30]<-0.281029342/10
DistEdad[31:40]<-0.30552628/10
DistEdad[41:50]<-0.112127906/10
DistEdad[51:85]<-0.070564755/35

Age<-85
years<-20


NoSem<-52
NumHSH<-892955-best_theta[1] #(INE)
NumHSHVIH<-best_theta[1]  #Encuesta hospitalaria

ACD4<-best_theta[2] #Distribucion de los pacientes por rango de CD4 (AIDS + CD4 <200, merged)
I7CD4<-best_theta[3] #200-350
Rest<-best_theta[4]   #>350
PropTR<-best_theta[5]

#Values 
G<-best_theta[6]  #Population growth rate 1/1000 anually

m<-read.csv("MortPobGen.csv", header=TRUE, sep=";")  #Mortality general population
mVIH235<-best_theta[7] #Mortality CD4 200-350; Alejos et al Medicine 2016
mVIH35<-best_theta[8]  #Mortality CD4 >350; Alejos et al Medicine 2016
mAIDS<-best_theta[9]   #Parastu et al PLOSone 2018
Cvh<-best_theta[10] #Partner change rate in the very high group 18-123/year Nichols et al. 2016
Ch<-best_theta[11]     #Partner change rate in the high group 5-18/year Nichols et al. 2016
Cl<-best_theta[12]   #Partner change rate in the low group 0.5-5/year Nichols et al. 2016
Cvl<-best_theta[13]  #Partner change rate in the very low group 0.04-0.5/year Nichols et al. 2016
nvh<-best_theta[14]     #Proportion of the total population in each group 5-15% Nichols et al. 2016
nh<-best_theta[15]     #30-50% Nichols et al. 2016
nl<-best_theta[16]     #10-35% Nichols et al. 2016
nvl<-best_theta[17]    #4-46%

B<-best_theta[18]  #per partnership transmissibility Nichols et al 2016.
I12<-best_theta[19] #1 month duration in stage 1 of HIV infection
I23<-best_theta[20] #1 month duration in stage 2 of HIV infection
I34<-best_theta[21] #1 month duration in stage 3 of HIV infection
I45<-best_theta[22] #3 month duration in stage 4 of HIV infection
I56<-best_theta[23] #3 month duration in stage 5 of HIV infection
I67<-best_theta[24] #Chronic duration in stage 6 of HIV infection
I78<-best_theta[25] #Chronic duration in stage 7 of HIV infection

PTr<-c(best_theta[26],best_theta[27],best_theta[28]) #Nuñez et al AIDS 2018
Woff      <- 0.0038 #Proportion of people who go off PrEP. SiPrEP 15% anual, p=1-e^-rt
W<-0.00192    #Proportion of people who go on PrEP. SiPrEP describe 5000-7000 nuevos anuales y eso supone una probabilidad alrededor de 0.1 anual.
```


####################################################################################################
#Simulating the scenario with TDF/FTC PrEP################
####################################################################################################

```{r}
source("HIVSIM05.R") #(With calibration changes and PrEP)
source("QALYCostP.R")
RiskRed<-1-0.86 # 0.86 for TDF, 0.96 for LCA

QP<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mVIH235, mVIH35, mAIDS,
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I56, I67, 
                 I78, PTr, years)

head(QP[[3]][1:9])
QQP<-array(unlist(QP), dim=c(52,ncol(QP[[1]]),years))
```

###Arranging the array into a megamatrix
```{r, echo=FALSE}
Q1P <- NULL

for (t in 1:years) {

  Qt <- QQP[1:52, , t]

  Q1P <- rbind(
    Q1P,
    data.frame(
      Weeks      = Qt[, 1],
      Susceptible= rowSums(Qt[,   2:341]),
      PrEP       = rowSums(Qt[, 342:511]),
      Inf1       = rowSums(Qt[, 512:1021]),
      Inf2       = rowSums(Qt[,1022:1531]),
      Inf3       = rowSums(Qt[,1532:2041]),
      Inf4       = rowSums(Qt[,2042:2551]),
      Inf5       = rowSums(Qt[,2552:3061]),
      Inf6       = rowSums(Qt[,3062:3571]),
      Inf7       = rowSums(Qt[,3572:4081]),
      AIDS       = rowSums(Qt[,4082:4591]),
      Treated    = rowSums(Qt[,4592:4676]),
      Dead       = rowSums(Qt[,4677:4761]),
      NewAIDS    = rowSums(Qt[,4762:4846]),
      FI_vh      = rowSums(Qt[,4847:4931]),
      FI_h       = rowSums(Qt[,4932:5016]),
      FI_l       = rowSums(Qt[,5017:5101]),
      FI_vl      = rowSums(Qt[,5102:5186]),
      NewHIV     = rowSums(Qt[,5187:5271])
    )
  )
}

Q1P$Weeks <- seq_len(nrow(Q1P))
```

##Evolucion estados individuales 20 años
```{r}
plot1<-ggplot(Q1P, aes(Weeks))+
    geom_line(aes(y=Susceptible, color="Susceptible"))+
    geom_line(aes(y=Inf1, colour="stage1"))+
    geom_line(aes(y=PrEP, color="PrEP"))+
    geom_line(aes(y=Inf2, color="stage2"))+
    geom_line(aes(y=Inf3, color="stage3"))+
    geom_line(aes(y=Inf4, color="stage4"))+
    geom_line(aes(y=Inf5, color="stage5"))+
    geom_line(aes(y=Inf6, color="stage6"))+
    geom_line(aes(y=Inf7, color="stage7"))+
    geom_line(aes(y=AIDS, color="AIDS"))+
    geom_line(aes(y=Treated, color="Treated"))+
    theme_classic()
plot1
```


##Nuevas infecciones
### Total de nuevas infecciones
```{r}
Q2P <- data.frame(Weeks = Q1P$Weeks, NewHIV = Q1P$NewHIV)

Q2P_year <- Q2P |>
  transform(Year = ((Weeks - 1) %/% 52) + 1) |>
  aggregate(NewHIV ~ Year, data = _, sum)

ggplot(Q2P_year, aes(x = Year, y = NewHIV)) +
  geom_point(size = 2) +
  ylim(0,10000)+
  geom_line() +
  theme_classic()
```
#### Numeros
```{r}
Total <- sum(Q1P$NewHIV, na.rm = TRUE)
PY <- sum(Q1P$Susceptible + Q1P$PrEP, na.rm = TRUE) / 52
incidence <- Total / PY * 1000
Total
incidence
```

```{r}
Q3P<-as.data.frame(cbind(Q1P[,1], rowSums(Q1P[,4:9])))
plot3<-ggplot(Q3P, aes(V1))+
    geom_line(aes(y=V2))
    #coord_cartesian(ylim =c(0, 3000), xlim = c(0, 520))
plot3
```
##Muertos
```{r}
Q4P<-as.data.frame(cbind(Q1P[,1], Q1P[,13]))
Q4P1<-Q4P[c(52*c(1:40)),]
#Q41c<-cbind(Q4P1,Q41[,2] )
plot4<-ggplot(Q4P, aes(V1/52))+
    geom_line(aes(y=V2, colour="with PrEP"))+
    #geom_line(aes(y=Q41[,2], colour="No PrEP"))+
    theme_classic()+
    scale_color_manual(name="Intervention", values = c("with PrEP" = "darkblue", "No PrEP" = "red"))
    #coord_cartesian(ylim =c(0, 100), xlim = c(0, 520))
plot4
```

##Calculo de los QALYs
```{r}
WAIDS<-0.7/52  
WHIV<-0.84/52
WM350<-0.94/52
WTREAT<-0.96/52    
WSusceptible<-1/52

#DALYsP<-sum(Q1P[,c("Inf1", "Inf2", "Inf3", "Inf4", "Inf5","Inf6", "Inf7", #"Inf8")])*WHIV+sum(Q1P[,"AIDS"]*WAIDS)+sum(Q1P[,"Treated"]*WTREAT)
QALYsP<-0

x<-Q1P[,c("Inf2", "Inf3", "Inf4", "Inf5","Inf6", "Inf7")]
for (i in 1:length(x)){QALYsP<-QALYsP+QalyCalc(x[,i],w=WM350)}
QALYsP<-QALYsP+QalyCalc(Q1P[,"Inf1"],w=WHIV)
QALYsP<-QALYsP+QalyCalc(Q1P[,"Susceptible"],w=WSusceptible)
QALYsP<-QALYsP+QalyCalc(Q1P[,"PrEP"],w=WSusceptible)
QALYsP<-QALYsP+QalyCalc(Q1P[,"AIDS"],w=WAIDS)
QALYsP<-QALYsP+QalyCalc(Q1P[,"Treated"],w=WTREAT)

QALYsP

```
##Cálculo de los costes
```{r}
Treatcost<-188.54
AIDScost<-19000/52
PrEPcost<- 26.34 # TDF/FTC 26.94, LCA 898.82

#AIDScostFinalP<-sum(Q1P[,"AIDS"])*AIDScost
#TreatmentNotAIDSFinalP<-sum(Q1P[,"Treated"])*Treatcost
#TotalPrEPcost<-sum(Q1P[,"PrEP"])*PrEPcost

#AIDScostFinalP
#TreatmentNotAIDSFinalP
#TotalPrEPcost

#CostsP<-sum(Q1P[,"AIDS"])*AIDScost+sum(Q1P[,"Treated"])*Treatcost+sum(Q1P[,"PrEP"])*PrEPcost
#CostsP

CostsP<-0
CostsP1<-0
CostsP2<-0
CostsP3<-0

CostsP1<-CostsP1+CostCalc(Q1P[,"AIDS"],C=AIDScost)
CostsP2<-CostsP2+CostCalc(Q1P[,"Treated"],C=Treatcost)
CostsP3<-CostsP3+CostCalc(Q1P[,"PrEP"],C=PrEPcost)
CostsP1
CostsP2
CostsP3
CostsP<-CostsP1+CostsP2+CostsP3
CostsP
```
####################################################################################################
#Simulating the scenario with LCP PrEP################
####################################################################################################

```{r}
source("HIVSIM05.R") # (With calibration changes and PrEP)
source("QALYCostP.R")

RiskRed<-1-0.96 # 0.86 for TDF, 0.96 for LCA

QLCA<-HIVSIMPREP(Age, NoSem, NumHSH, NumHSHVIH, 
                 ACD4, I7CD4, Rest, 
                 G, Woff, W, 
                 m, mVIH235, mVIH35, mAIDS,
                 Cvh, Ch, Cl, Cvl, 
                 nvh, nh, nl, nvl, B,
                 I12, I23, I34, 
                 I45, I56, I67, 
                 I78, PTr, years, RiskRed=1-0.96)

head(QLCA[[3]][1:9])
QQLCA<-array(unlist(QLCA), dim=c(52,5271,years))
```

###Arranging the array into a megamatrix
```{r, echo=FALSE}
Q1LCA <- NULL

for (t in 1:years) {

  Qt <- QQLCA[1:52, , t]

  Q1LCA <- rbind(
    Q1LCA,
    data.frame(
      Weeks      = Qt[, 1],
      Susceptible= rowSums(Qt[,   2:341]),
      PrEP       = rowSums(Qt[, 342:511]),
      Inf1       = rowSums(Qt[, 512:1021]),
      Inf2       = rowSums(Qt[,1022:1531]),
      Inf3       = rowSums(Qt[,1532:2041]),
      Inf4       = rowSums(Qt[,2042:2551]),
      Inf5       = rowSums(Qt[,2552:3061]),
      Inf6       = rowSums(Qt[,3062:3571]),
      Inf7       = rowSums(Qt[,3572:4081]),
      AIDS       = rowSums(Qt[,4082:4591]),
      Treated    = rowSums(Qt[,4592:4676]),
      Dead       = rowSums(Qt[,4677:4761]),
      NewAIDS    = rowSums(Qt[,4762:4846]),
      FI_vh      = rowSums(Qt[,4847:4931]),
      FI_h       = rowSums(Qt[,4932:5016]),
      FI_l       = rowSums(Qt[,5017:5101]),
      FI_vl      = rowSums(Qt[,5102:5186]),
      NewHIV     = rowSums(Qt[,5187:5271])
    )
  )
}

Q1LCA$Weeks <- seq_len(nrow(Q1LCA))
```


##Evolucion estados individuales 2 ano
```{r}
plot1<-ggplot(Q1LCA, aes(Weeks))+
    geom_line(aes(y=Susceptible, color="Susceptible"))+
    geom_line(aes(y=Inf1, colour="stage1"))+
    geom_line(aes(y=PrEP, color="PrEP"))+
    #geom_line(aes(y=Inf2, color="stage2"))+
    #geom_line(aes(y=Inf3, color="stage3"))+
    #geom_line(aes(y=Inf4, color="stage4"))+
    #geom_line(aes(y=Inf5, color="stage5"))+
    #geom_line(aes(y=Inf6, color="stage6"))+
    #geom_line(aes(y=Inf7, color="stage7"))+
    #geom_line(aes(y=Inf8, color="stage8"))+
    geom_line(aes(y=AIDS, color="AIDS"))+
    geom_line(aes(y=Treated, color="Treated"))
plot1
```

##Número total de VIH sin tto
```{r}
Q2LCA<-as.data.frame(cbind(Q1LCA[,1], rowSums(Q1LCA[,4:11])))
plot2<-ggplot(Q2LCA, aes(V1))+
    geom_line(aes(y=V2, color="red"))
    #coord_cartesian(ylim =c(0, 1000), xlim = c(0, 520))
plot2
```
##Nuevas infecciones
### Total de nuevas infecciones
```{r}
Q2LCA <- data.frame(Weeks = Q1LCA$Weeks, NewHIV = Q1LCA$NewHIV)

Q2LCA_year <- Q2LCA |>
  transform(Year = ((Weeks - 1) %/% 52) + 1) |>
  aggregate(NewHIV ~ Year, data = _, sum)

ggplot(Q2LCA_year, aes(x = Year, y = NewHIV)) +
  geom_point(size = 2) +
  geom_line() +
  ylim(0,10000)+
  theme_classic()
```
### Total de nuevas infecciones
```{r}
Total <- sum(Q1LCA$NewHIV, na.rm = TRUE)
PY <- sum(Q1LCA$Susceptible + Q1LCA$PrEP, na.rm = TRUE) / 52
incidence <- Total / PY * 1000
Total
incidence
```

```{r}
Q3LCA<-as.data.frame(cbind(Q1LCA[,1], rowSums(Q1LCA[,4:9])))
plot3<-ggplot(Q3LCA, aes(V1))+
    geom_line(aes(y=V2))
    #coord_cartesian(ylim =c(0, 3000), xlim = c(0, 520))
plot3
```
##Muertos
```{r}
Q4LCA<-as.data.frame(cbind(Q1LCA[,1], Q1LCA[,13]))
#Q4P1<-Q4P[c(52*c(1:20)),]
#Q41c<-cbind(Q4P1,Q41[,2] )
plot4<-ggplot(Q4LCA, aes(V1/52))+
    geom_line(aes(y=V2, colour="with PrEP"))+
    theme_classic()+
    scale_color_manual(name="Intervention", values = c("with PrEP" = "darkblue", "No PrEP" = "red"))
    #coord_cartesian(ylim =c(0, 100), xlim = c(0, 520))
plot4
```

##Calculo de los QALYs
```{r}
WAIDS<-0.7/52  
WHIV<-0.84/52
WM350<-0.94/52
WTREAT<-0.96/52    
WSusceptible<-1/52

#DALYsP<-sum(Q1LCA[,c("Inf1", "Inf2", "Inf3", "Inf4", "Inf5","Inf6", "Inf7", #"Inf8")])*WHIV+sum(Q1LCA[,"AIDS"]*WAIDS)+sum(Q1LCA[,"Treated"]*WTREAT)
QALYsLCA<-0

x<-Q1LCA[,c("Inf2", "Inf3", "Inf4", "Inf5","Inf6", "Inf7")]
for (i in 1:length(x)){QALYsLCA<-QALYsLCA+QalyCalc(x[,i],w=WM350)}
QALYsLCA<-QALYsLCA+QalyCalc(Q1LCA[,"Inf1"],w=WHIV)
QALYsLCA<-QALYsLCA+QalyCalc(Q1LCA[,"Susceptible"],w=WSusceptible)
QALYsLCA<-QALYsLCA+QalyCalc(Q1LCA[,"PrEP"],w=WSusceptible)
QALYsLCA<-QALYsLCA+QalyCalc(Q1LCA[,"AIDS"],w=WAIDS)
QALYsLCA<-QALYsLCA+QalyCalc(Q1LCA[,"Treated"],w=WTREAT)


QALYsLCA

```
##Cálculo de los costes
```{r}
Treatcost<-188.54
AIDScost<-19000/52
PrEPcost<- 898.25 # TDF/FTC 26.94, LCA 898.25  LCA_2 390, LCA 3 195, LCA 4 98
#LCA 5 49, LCA 6 28.95, LCAMAX 30.5


CostsLCA<-0
CostsLCA1<-0
CostsLCA2<-0
CostsLCA3<-0

CostsLCA1<-CostsLCA1+CostCalc(Q1LCA[,"AIDS"],C=AIDScost)
CostsLCA2<-CostsLCA2+CostCalc(Q1LCA[,"Treated"],C=Treatcost)
CostsLCA3<-CostsLCA3+CostCalc(Q1LCA[,"PrEP"],C=PrEPcost)
CostsLCA1
CostsLCA2
CostsLCA3
CostsLCA<-CostsLCA1+CostsLCA2+CostsLCA3
CostsLCA
```
##########################################################################
##########################################################################
# Análisis de coste-eficacia
```{r}
CostDiff<-CostsLCA-CostsP
Cost<-cbind(CostsLCA, CostsP, CostDiff)
QalyDiff<-QALYsLCA-QALYsP
QALY<-cbind(QALYsLCA, QALYsP, QalyDiff)
ICER<-CostDiff/QalyDiff
Result<-list(Cost, QALY, ICER)
names(Result)<-c("Cost", "QALY", "ICER")
save(Result, file="Result_TDFLCA_LHS_2")
Result  # GDP per capita of Spain 33395.59€ https://www.statista.com/statistics/263773/gross-domestic-product-gdp-per-capita-in-spain/

```
# Summary

```{r}
rm(Result)
load("Result_TDFLCA_LHS_2")
TDFLCA<-Result
rm(Result)
```
# CE plane
```{r}
results<-c("TDF_PrEP", AQalys=0, ACosts=0, "LCA_PreP", TDFLCA[[2]][3], TDFLCA[[1]][3])
table4<-matrix(results, ncol=3, byrow=TRUE)
colnames(table4)<-c("Intervention", "QALY_difference", "COST_difference")
table4<-as.data.frame(table4)
table4$QALY_difference<-as.numeric(table4$QALY_difference)
table4$COST_difference<-as.numeric(table4$COST_difference)
table4
```
```{r}

g1<-ggplot(table4, aes(x=QALY_difference, y=COST_difference, color=Intervention))+
  geom_point(size=3)+
  ggtitle("Cost-Effectiveness Analysis of PrEP")+
  geom_hline(yintercept =0)+
  geom_vline(xintercept =0)+
  #scale_x_log10()+
  #scale_y_log10()+
  ylab("Incremental Costs in 2023 €")+
  xlab("Incremental QALYs")+
  theme_classic()+
  theme(plot.title = element_text(hjust = 0.5))+
  geom_abline(slope=33395, color="red")

#Statista. Gross domestic product (GDP) per capita in Spain 2029 [Internet]. 2024 Dec [cited 2025 #Feb 9]. Available from: https://www.statista.com/statistics/263773/gross-domestic-product-gdp-per-c#apita-in-spain/           

#tiff("CEA_1.tiff", width=16, height=12, units="cm", res=300)
g1
#dev.off

```

##########################################################################
##########################################################################
# Price-seeking analysis: maximum cost-effective price for lenacapavir

```{r}
# Since CostCalc is linear in C, we can express the discounted PrEP
# person-weeks as a single scalar and solve for the threshold price.
# ICER = WTP  =>  (CostsLCA(price) - CostsP) / QalyDiff = WTP
# Rearranging: price = (WTP * QalyDiff + CostsP - CostsLCA1 - CostsLCA2) /
#                       discounted_PrEP_person_weeks

discounted_prep_pw <- CostCalc(Q1LCA[, "PrEP"], C = 1)

wtp_thresholds <- c(
  `1x GDP/cap`  = 33395.59
)

threshold_prices <- sapply(wtp_thresholds, function(wtp) {
  (wtp * QalyDiff + CostsP - CostsLCA1 - CostsLCA2) / discounted_prep_pw
})

price_df <- data.frame(
  WTP_threshold   = names(wtp_thresholds),
  WTP_value       = unname(wtp_thresholds),
  Max_weekly_price = unname(threshold_prices),
  Max_6monthsdose_price = unname(threshold_prices) * 26,
  Max_annual_price = unname(threshold_prices) * 52
)

price_df
```

```{r}
# Visualise ICER as a function of LCA weekly price
current_len_price <- 898.25
price_max  <- current_len_price * 1.15
price_grid <- seq(0, price_max, length.out = 500)

icer_by_price <- sapply(price_grid, function(p) {
  cost_lca_at_p <- CostsLCA1 + CostsLCA2 + discounted_prep_pw * p
  (cost_lca_at_p - CostsP) / QalyDiff
})

icer_df <- data.frame(Weekly_price = price_grid, ICER = icer_by_price)

icer_at_current   <- (CostsLCA1 + CostsLCA2 + discounted_prep_pw * current_len_price - CostsP) / QalyDiff
icer_at_threshold <- unname(wtp_thresholds)

g2 <- ggplot(icer_df, aes(x = Weekly_price, y = ICER)) +
  geom_line(linewidth = 0.8) +
  geom_segment(
    data = data.frame(
      x = threshold_prices, xend = threshold_prices,
      y = 0, yend = icer_at_threshold
    ),
    aes(x = x, xend = xend, y = y, yend = yend),
    linetype = "dotted", colour = "forestgreen", inherit.aes = FALSE
  ) +
  geom_segment(
    data = data.frame(
      x = 0, xend = threshold_prices,
      y = icer_at_threshold, yend = icer_at_threshold
    ),
    aes(x = x, xend = xend, y = y, yend = yend),
    linetype = "dotted", colour = "forestgreen", inherit.aes = FALSE
  ) +
  geom_point(
    data = data.frame(x = threshold_prices, y = icer_at_threshold),
    aes(x = x, y = y), size = 2.5, colour = "forestgreen",
    shape = 18, inherit.aes = FALSE
  ) +
  annotate("text",
           x = threshold_prices, y = icer_at_threshold,
           label = paste0(
             names(wtp_thresholds),
             " (", round(threshold_prices, 1), " \u20ac/wk)"
           ),
           hjust = -0.08, vjust = -0.8,
           size = 3, colour = "forestgreen") +
  geom_point(
    data = data.frame(x = current_len_price, y = icer_at_current),
    aes(x = x, y = y), size = 3, colour = "red", inherit.aes = FALSE
  ) +
  geom_segment(
    aes(x = current_len_price, xend = current_len_price,
        y = 0, yend = icer_at_current),
    linetype = "dotted", colour = "red", inherit.aes = FALSE
  ) +
  annotate("text",
           x = current_len_price, y = icer_at_current,
           label = paste0(
             "Current price (",
             format(current_len_price, big.mark = ","), " \u20ac/wk)\n",
             "ICER = ", format(round(icer_at_current), big.mark = ","),
             " \u20ac/QALY"
           ),
           hjust = 1.05, vjust = -0.3,
           size = 3, colour = "red") +
  scale_x_continuous(labels = scales::comma) +
  scale_y_continuous(labels = scales::comma) +
  labs(x = "Lenacapavir weekly cost (\u20ac)",
       y = "ICER (\u20ac/QALY)",
       title = "ICER vs lenacapavir price (LEN vs TDF/FTC)") +
  theme_classic() +
  theme(plot.title = element_text(hjust = 0.5))

g2
```
```{r}
ggplot(Q2P_year, aes(x = Year, y = NewHIV)) +
  geom_point(size = 2) +
  ylim(0,10000)+
  geom_line() +
  theme_classic()

ggplot(Q2LCA_year, aes(x = Year, y = NewHIV)) +
  geom_point(size = 2) +
  geom_line() +
  ylim(0,10000)+
  theme_classic()

```