---
title: "PrEP CEA – Paired PSA (LEN vs TDF)"
author: "Philip Wikman"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(dplyr)
library(parallel)
library(tidyr)
library(DirichletReg)
library(BCEA)
source("invbeta.R")
source("invgamma.R")
source("HIVSIM05.R")
source("QalyCalc.R")
source("CostCalc.R")
source("QALYCostP.R")
```

# Load best-fit parameters
```{r}
load("Best_theta_Param")
```

# Paired PSA: both arms share common parameter draws

All shared epidemic parameters
are drawn **once** per iteration and used for both the TDF and LEN arms.
Only `RiskRed` and `PrEPcost` differ between arms.

```{r psa-setup}
repeats <- 50 # per core

DistEdad <- vector(length = 85)
DistEdad[1:10]  <- 0.114106384 / 10
DistEdad[11:20] <- 0.116645332 / 10
DistEdad[21:30] <- 0.281029342 / 10
DistEdad[31:40] <- 0.30552628  / 10
DistEdad[41:50] <- 0.112127906 / 10
DistEdad[51:85] <- 0.070564755 / 35

Age    <- 85
years  <- 20
NoSem  <- 52

# QALY weights (weekly)
WAIDS        <- 0.7  / 52
WHIV         <- 0.84 / 52
WM350        <- 0.94 / 52
WTREAT       <- 0.96 / 52
WSusceptible <- 1    / 52

# Costs shared across arms
Treatcost <- 188.54
AIDScost  <- 19000 / 52

# PrEP costs (arm-specific)
PrEPcost_TDF <- 26.34
PrEPcost_LEN <- 898.25

m <- read.csv("MortPobGen.csv", header = TRUE, sep = ";")

Woff <- 0.0038
W    <- 0.00192
```

```{r psa-function}
PSA_paired <- function(repeats) {
  MAT_TDF <- matrix(NA, nrow = repeats, ncol = 2)
  MAT_LEN <- matrix(NA, nrow = repeats, ncol = 2)
  disc_pw  <- numeric(repeats)

  for (i in 1:repeats) {
    # ── Draw shared parameters ONCE ──────────────────────────────────────
    NumHSHVIH <- rnorm(1, best_theta[1], 4000)
    NumHSH    <- 892955 - NumHSHVIH

    j     <- rdirichlet(1, c(best_theta[2], best_theta[3], best_theta[4]))
    ACD4  <- j[1]
    I7CD4 <- j[2]
    Rest  <- j[3]

    PropTR <- invbeta(best_theta[5], best_theta[5] * 0.1)
    G      <- rnorm(1, best_theta[6], best_theta[6] * 0.2)

    mVIH235 <- rnorm(1, best_theta[7],  best_theta[7]  * 0.2)
    mVIH35  <- rnorm(1, best_theta[8],  best_theta[8]  * 0.2)
    mAIDS   <- rnorm(1, best_theta[9],  best_theta[9]  * 0.2)
    Cvh     <- rnorm(1, best_theta[10], best_theta[10] * 0.2)
    Ch      <- rnorm(1, best_theta[11], best_theta[11] * 0.2)
    Cl      <- rnorm(1, best_theta[12], best_theta[12] * 0.2)
    Cvl     <- rnorm(1, best_theta[13], best_theta[13] * 0.2)

    j1  <- rdirichlet(1, c(best_theta[14], best_theta[15],
                            best_theta[16], best_theta[17])) * 10
    nvh <- j1[1]
    nh  <- j1[2]
    nl  <- j1[3]
    nvl <- j1[4]

    # PrEP programme parameters (shared across arms)
    W    <- invbeta(0.00192, 0.00192 * 0.2)
    Woff <- invbeta(0.0038,  0.0038  * 0.2)

    B   <- rnorm(1, best_theta[18], best_theta[18] * 0.02)
    I12 <- invbeta(best_theta[19], best_theta[19] * 0.2)
    I23 <- invbeta(best_theta[20], best_theta[20] * 0.2)
    I34 <- invbeta(best_theta[21], best_theta[21] * 0.2)
    I45 <- invbeta(best_theta[22], best_theta[22] * 0.2)
    I56 <- invbeta(best_theta[23], best_theta[23] * 0.2)
    I67 <- invbeta(best_theta[24], best_theta[24] * 0.2)
    I78 <- invbeta(best_theta[25], best_theta[25] * 0.2)
    PTr <- c(invbeta(best_theta[26], best_theta[26] * 0.2),
             invbeta(best_theta[27], best_theta[27] * 0.2),
             invbeta(best_theta[28], best_theta[28] * 0.2))

    # ── Draw arm-specific RiskRed ────────────────────────────────────────
    # SE derived from trial CIs
    RiskRed_TDF <- 1 - invbeta(0.86, 0.0973)   # TDF 90% CI [0.64, 0.96]
    RiskRed_LEN <- 1 - invbeta(0.96, 0.0434)   # LEN 95% CI [0.82, 0.99]

    # Shared arguments for HIVSIMPREP
    shared <- list(
      Age = Age, NoSem = NoSem, NumHSH = NumHSH, NumHSHVIH = NumHSHVIH,
      ACD4 = ACD4, I7CD4 = I7CD4, Rest = Rest,
      G = G, Woff = Woff, W = W,
      m = m, mVIH235 = mVIH235, mVIH35 = mVIH35, mAIDS = mAIDS,
      Cvh = Cvh, Ch = Ch, Cl = Cl, Cvl = Cvl,
      nvh = nvh, nh = nh, nl = nl, nvl = nvl, B = B,
      I12 = I12, I23 = I23, I34 = I34,
      I45 = I45, I56 = I56, I67 = I67,
      I78 = I78, PTr = PTr, years = years, PropTR = PropTR
    )

    # ── TDF arm ──────────────────────────────────────────────────────────
    PrEPcost <<- PrEPcost_TDF
    Q_TDF <- do.call(HIVSIMPREP, c(shared, list(RiskRed = RiskRed_TDF)))
    MAT_TDF[i, ] <- QALYCostP(Q_TDF)

    # ── LEN arm ──────────────────────────────────────────────────────────
    PrEPcost <<- PrEPcost_LEN
    Q_LEN <- do.call(HIVSIMPREP, c(shared, list(RiskRed = RiskRed_LEN)))
    MAT_LEN[i, ] <- QALYCostP(Q_LEN)

    # Discounted PrEP person-weeks (for threshold price analysis)
    PrEPcost <<- 0
    costs_no_prep <- QALYCostP(Q_LEN)[, 2]
    disc_pw[i] <- (MAT_LEN[i, 2] - costs_no_prep) / PrEPcost_LEN
  }

  cbind(MAT_TDF, MAT_LEN, disc_pw)
}
```

```{r run-psa}
ncores <- detectCores()
cl <- makeCluster(ncores, type = "PSOCK")
clusterSetRNGStream(cl, iseed = 1)
clusterExport(cl, c(
  "best_theta", "DistEdad", "Age", "years", "NoSem",
  "WAIDS", "WHIV", "WM350", "WTREAT", "WSusceptible",
  "Treatcost", "AIDScost", "PrEPcost_TDF", "PrEPcost_LEN",
  "QALYCostP", "invbeta", "QalyCalc", "HIVSIMPREP",
  "PSA_paired", "CostCalc", "rdirichlet", "W", "Woff", "m"
))

results <- clusterCall(cl, fun = PSA_paired, repeats)
stopCluster(cl)

# Assemble results from all cores
x <- do.call(rbind, results)
MAT2     <- cbind(x[, 1:2], "PrEP-TDF")
MAT2P3   <- cbind(x[, 3:4], "PREP-LEN")
disc_pw_vec <- as.numeric(x[, 5])

save(MAT2,       file = "MAT2_LHS_R")
save(MAT2P3,     file = "MAT2LEN_R")
save(disc_pw_vec, file = "disc_pw_vec_R")
```

```{r incremental}
PSADATA1 <- tibble(
  QalysLEN = as.numeric(x[, 3]),
  CostsLEN = as.numeric(x[, 4]),
  QalysTDF = as.numeric(x[, 1]),
  CostsTDF = as.numeric(x[, 2]),
  disc_pw  = as.numeric(x[, 5]),
  AQalys   = QalysLEN - QalysTDF,
  ACosts   = CostsLEN - CostsTDF,
  ICERS    = ACosts / AQalys
) |>
  filter(complete.cases(pick(everything())))

PSADATA1
```

# ICER summary
```{r icer-summary}
# Ratio of means — the correct PSA summary statistic for ICERs
# (the mean of individual ICERs is unreliable due to Jensen's inequality
# when ΔQALYs is near zero in many iterations)
icer_ratio_of_means <- mean(PSADATA1$ACosts) / mean(PSADATA1$AQalys)
cat("ICER (ratio of means, E[ΔC]/E[ΔQ]):",
    format(round(icer_ratio_of_means), big.mark = ","), "\n")

# Summary of incremental costs and QALYs (more informative than
# individual ICERs, which are unstable when ΔQALYs is near zero)
cat("--- Incremental QALYs (LEN - TDF) ---\n")
summary(PSADATA1$AQalys)
cat("\n--- Incremental Costs (LEN - TDF) ---\n")
summary(PSADATA1$ACosts)

# Probability cost-effective at Spain WTP threshold
p_ce_spain <- mean(33395.59 * PSADATA1$AQalys - PSADATA1$ACosts > 0, na.rm = TRUE)
cat("\nP(cost-effective) at WTP = €33,395/QALY:", p_ce_spain, "\n")
```


```{r ce-plane}
x_label_pos <- max(PSADATA1$AQalys, na.rm = TRUE) * 0.72

ggplot(PSADATA1, aes(AQalys, ACosts)) +
  geom_point(alpha = 0.4, size = 1, color = "red") +
  geom_hline(yintercept = 0, color = "grey40") +
  geom_vline(xintercept = 0, color = "grey40") +
  geom_abline(slope = 33895.59, intercept = 0, color = "red", linetype = "dotted") +
  scale_x_continuous(labels = scales::comma) +
  scale_y_continuous(labels = scales::comma) +
  labs(
    title = "Cost-effectiveness plane (paired PSA)",
    x     = "Incremental QALYs (LEN \u2212 TDF)",
    y     = "Incremental costs (LEN \u2212 TDF, 2023 \u20ac)"
  ) +
  theme_classic() +
  theme(plot.title = element_text(hjust = 0.5))
```

```{r ceac}
wtp_seq <- seq(0, 150000, by = 500)

ceac <- tibble(
  wtp  = wtp_seq,
  p_ce = sapply(wtp_seq, function(lambda) {
    mean(lambda * PSADATA1$AQalys - PSADATA1$ACosts > 0, na.rm = TRUE)
  })
)

ggplot(ceac, aes(x = wtp, y = p_ce)) +
  geom_line(color = "red", linewidth = 0.9) +
  geom_hline(yintercept = 0.5, linetype = "dashed", color = "grey50") +
  geom_vline(xintercept = 33395.59, color = "red", linetype = "dotted") +
  scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.1)) +
  scale_x_continuous(labels = scales::comma) +
  labs(
    title = "CEAC (paired PSA)",
    x     = "Willingness to pay (2023 \u20ac/QALY)",
    y     = "Probability cost-effective"
  ) +
  theme_classic() +
  theme(plot.title = element_text(hjust = 0.5))
```

# Threshold price analysis

For each PSA iteration, the maximum weekly LEN price at which it would be
cost-effective at the Spanish WTP threshold (€33,395/QALY):

$$P^* = P_{\text{LEN}} + \frac{\text{WTP} \cdot \Delta Q - \Delta C}{D_{\text{LEN}}}$$

```{r threshold-price}
wtp_spain <- 33395.59

threshold_price <- PrEPcost_LEN +
  (wtp_spain * PSADATA1$AQalys - PSADATA1$ACosts) / PSADATA1$disc_pw

tp_finite <- threshold_price[is.finite(threshold_price)]

tp_summary <- tibble(
  Statistic       = c("Mean", "P5", "Median", "P95"),
  `€/week`        = c(mean(tp_finite), quantile(tp_finite, 0.05),
                       median(tp_finite), quantile(tp_finite, 0.95)),
  `€/6-month dose` = `€/week` * 26,
  `€/year`        = `€/week` * 52
) |>
  mutate(across(where(is.numeric), \(x) round(x, 2)))

tp_summary

cat("\nCurrent LEN price:", PrEPcost_LEN, "€/wk (",
    round(PrEPcost_LEN * 26, 2), "€/6-month dose,",
    round(PrEPcost_LEN * 52, 2), "€/year )\n")
```

```{r threshold-price-plot}
tp_df <- data.frame(threshold_price = threshold_price[is.finite(threshold_price)])

ggplot(tp_df, aes(x = threshold_price)) +
  geom_histogram(bins = 40, fill = "steelblue", colour = "white", alpha = 0.8) +
  geom_vline(xintercept = PrEPcost_LEN, colour = "red", linetype = "dashed") +
  annotate("text", x = PrEPcost_LEN, y = Inf,
           label = paste0("Current price (", PrEPcost_LEN, " €/wk)"),
           hjust = 1.05, vjust = 2, colour = "red", size = 3.5) +
  geom_vline(xintercept = median(tp_df$threshold_price, na.rm = TRUE),
             colour = "steelblue", linetype = "dashed") +
  annotate("text",
           x = median(tp_df$threshold_price, na.rm = TRUE), y = Inf,
           label = paste0("Median (", round(median(tp_df$threshold_price, na.rm = TRUE), 1), " €/wk)"),
           hjust = -0.05, vjust = 2, colour = "steelblue", size = 3.5) +
  scale_x_log10(labels = scales::comma) +
  labs(
    title = "Distribution of threshold LEN weekly price for cost-effectiveness",
    subtitle = paste0("WTP = ", format(wtp_spain, big.mark = ","), " €/QALY"),
    x = "Maximum weekly LEN price (€)",
    y = "Count"
  ) +
  theme_classic() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5))
```

```{r diagnostics}
cat("Correlation (QALYs):", cor(PSADATA1$QalysTDF, PSADATA1$QalysLEN), "\n")
cat("Correlation (Costs):", cor(PSADATA1$CostsTDF, PSADATA1$CostsLEN), "\n\n")

cat("CE plane quadrant distribution:\n")
cat("  NE (trade-off):  ", mean(PSADATA1$ACosts > 0 & PSADATA1$AQalys > 0), "\n")
cat("  NW (dominated):  ", mean(PSADATA1$ACosts > 0 & PSADATA1$AQalys < 0), "\n")
cat("  SE (dominant):   ", mean(PSADATA1$ACosts < 0 & PSADATA1$AQalys > 0), "\n")
cat("  SW (trade-off):  ", mean(PSADATA1$ACosts < 0 & PSADATA1$AQalys < 0), "\n")
```
